### 2011-12-25 paper.tex
Initial commit

\documentclass[titlepage, a4paper, 12pt]{article}
\usepackage{listings}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[colorlinks=false]{hyperref}
\lstset{ %
language=sh,
basicstyle=\footnotesize,
numbers=none,
backgroundcolor=\color{white},
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=b,
breaklines=true,
breakatwhitespace=false,
title=\lstname
}
\title{Apropos Replacement \newline
(Extended  Abstract)}
\author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
Joerg Sonnenberger $<$joerg@netbsd.org$>$}
\begin{document}
\maketitle
\section{Abstract}
Unix like operating systems have withstood the test of time for 50 odd years for
several technical and philosophical reasons and one of those reasons is the
quality documentation they ship in the form of man pages. They are a single point
source of consultation for most of our routine work. But there has been a lack of
good search tool to accompany this documentation which would increase their
usefulness manifolds.

Traditionally \textit{apropos(1)} [1] has been there to act as a search
interface but to a
large extent it hasn't really lived up to it's expectation. \textit{\textit{apropos(1)}} was
developed in the early days of Unix when computing resources were scarce and
therefore we believe it was the primary reason that it's design was kept so
minimal and simple.

In this paper we discuss the limitations of the traditional implementation of
\textit{\textit{\textit{apropos(1)}(1)}}, how did we solve those limitations in our implementation
and what other modern implementations are available out there
our own implementation.
\section{Introduction}
The classical version of \textit{apropos(1)} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.

This simplified design of \textit{apropos(1)} resulted in limited utility and usability.
The searches are limited to the keywords in the NAME section of the keywords. If
only a user knows the exact keywords he gets the right results otherwise most of
the times the searches are full of bogus results or a dead end. In the modern
computing world where hard problems like searching the World Wide Web have been
solved [3] to sufficient degree where most of the data is unstructured, then it
makes perfect sense that we leverage the advancement in technology to solve the
problem of an effective man page search tool. In present time we have
powerful machines capable of running the search algorithms efficiently and disk
space is cheap enough that we can afford to index additional metadata from man
pages, which are a necessary prerequisite for an effective search tool.

\section{Limitations of Conventional \textit{apropos(1)}}
In this section we will see results of some sample query searches from
the classical version of \textit{apropos(1)} and analyze its shortcomings.

\subsection{Lack of support for free form queries}
The conventional \textit{apropos(1)} is limited to the keywords used in the NAME section
of the man pages. If the user specifies keywords relevant to the page that he
is looking but probably not used in it's NAME section, \textit{apropos(1)} would not return
anything relevant. So in essence the user cannot use free form queries like
supported by modern search applications.
\lstset{language = sh, caption={No results for free form queries}}
\begin{lstlisting}
$ \textit{apropos(1)} ``add new user''
adding new user: nothing appropriate

$ \textit{apropos(1)} ``get process status''
get process status: nothing appropriate

$ \textit{apropos(1)} ``termcap database''
termcap database: nothing appropriate

$ \textit{apropos(1)} ``signal number to string''
signal number to string: nothing appropriate
\end{lstlisting}

\subsection{Lack of basic language support}
Another major limitation of the classical version of \textit{apropos(1)} is that
it has no
natural language support. For example in the following listing we can see that
while \textit{apropos(1)} returns the correct result for the query \textit{``make directories''} but it fails when we use the keyword \textit{``directory''}
in place of \textit{``directories''} although the two words are based on same
root word.
\lstset{language = sh, caption={No support for stems or word with same roots},}
\begin{lstlisting}
$ \textit{apropos(1)} ``make directories''
mkdir (1) - make directories
$ \textit{apropos(1)} ``make directory''
make directory: nothing appropriate

$ \textit{apropos(1)} "upgrading software package"
pkg_add (1) - a utility for installing and upgrading software package
distributions
$ \textit{apropos(1)} "upgrading software packages"
upgrading software packages: nothing appropriate
\end{lstlisting}

Similarly, it is very common for users to misspell keywords in a query and the
classical \textit{apropos(1)} has no support for it either.
\lstset{language = sh, caption={No spelling correction},}
\begin{lstlisting}
$ \textit{apropos(1)} ``copy strings''
stpcpy, stpncpy, strcpy, strncpy (3) - copy strings
$ \textit{apropos(1)} ``coppy strings''
coppy strings: nothing appropriate
\end{lstlisting}

\subsection{Unintelligible Output}
Because the way \textit{apropos(1)} works, sometimes it's output can be unintelligible and
it can be very hard to find the results which are relevant to the user.
\lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},}
\begin{lstlisting}
$ \textit{apropos(1)} power
PCI, pci_activate, pci_bus_devorder, pci_chipset_tag_create,
pci_chipset_tag_destroy, pci_conf_read, pci_conf_write,
pci_conf_print, pci_conf_capture, pci_conf_restore, pci_find_device,
pci_get_capability, pci_mapreg_type, pci_mapreg_map, pci_mapreg_info,
pci_intr_map, pci_intr_string, pci_intr_evcnt, pci_intr_establish,
pci_intr_disestablish, pci_get_powerstate, pci_set_powerstate,
pci_vpd_read, pci_vpd_write, pci_make_tag, pci_decompose_tag,
pci_findvendor, pci_devinfo, PCI_VENDOR, PCI_PRODUCT, PCI_REVISION (9)
- Peripheral Component Interconnect
PMF, pmf_device_register, pmf_device_register1, pmf_device_deregister,
pmf_device_suspend, pmf_device_resume, pmf_device_recursive_suspend,
pmf_device_recursive_resume, pmf_device_resume_subtree,
pmf_class_network_register, pmf_class_input_register,
pmf_class_display_register, pmf_system_suspend, pmf_system_resume,
pmf_system_shutdown, pmf_event_register, pmf_event_deregister,
pmf_event_inject, pmf_set_platform, pmf_get_platform (9) - power
management and inter-driver messaging framework
acpi (4) - Advanced Configuration and Power Interface
acpipmtr (4) - ACPI Power Meter
amdpm (4) - AMD768 Power Management Controller and AMD8111 System
Management Controller
...
.
.
.
\end{lstlisting}
\subsection{Other Problems}
Apart from the search related problems there are a few issues related to
the way man pages are handled in NetBSD. The different aliases of the man pages
are stored on the filesystem in the from of hard (or soft) links and these
have to be mentioned in the makefiles explicitly using the MKLINK flag. This
approach works fine but we feel it is a mess from maintenance point of view.
When \textit{apropos(1)} maintains an index of the man page metadata then it
should be possible to fix this mess by utilizing that index. But yet again, the
simplistic implementation of \textit{apropos(1)} does not leave any room for
improvement.

\section{Proposed Solution}
We propose a simple and straightforward solution. The idea is to parse and index
the complete content (or at least most of the content) in the form of an
inverted index {4} and use it to build a full text search
interface. Having an index based on the complete content of the man pages solves
many of the search
related problems associated with the conventional \textit{apropos(1)} as noted
before and discussed as follows:
\begin{description}
\item[Free Form Queries] \hfill \\
The users can express their queries in more natural language form as the searches
are no longer limited to the keywords defined in the NAME section of the man
pages, the keywords used throughout the body of the page also play a role.
For example queries like \textit{``installing new software package''}
will get you the results.
\end{description}
\begin{description}
\item[Basic Natural Language Processing Support] \hfill \\
When parsing the man pages and building the index, it is also possible to
pre-process the tokens extracted from the man page to support some of the
basic natural language processing functionalities. We have used stemming [5] to
reduce the individual tokens extracted from the man pages to their root words.
This allows us to support more flexible searches. For example both
\textit{``Installing new packages''} and \textit{``install new package''} will
return same results.

Similarly along with the inverted index, we can also build a dictionary of the
keywords frequently occurring in the corpus of man pages and use it to support
spelling correction.

We have used both word stemming and spelling correction in our implementation to
make the search experience more smooth.
\end{description}
\begin{description}
\item[Bookkeeping of man page metadata] \hfill \\
In our implementation we have gone ahead and also indexed additional metadata
related to the man pages, for example we are indexing an md5 hash of the man
page, the device id, inode number and modification time of the man page file so
as to support incremental updating of the index as new man pages are installed
or the old ones are modified/updated.

Similarly we are also maintaining a separate index of all the aliases of a man
page. This will allow us to get rid of all the hard or symbolic links of the man
pages which are scattered throughout the filesystem, and also help in getting rid
of the MKLINK flags in the makefiles.
\end{description}
\subsection{Tools Used}
The two main tasks that we needed to perform were parsing of the man pages and
building an index of the data, and to do these tasks we have used \textit{libmandoc} [6]
and \textit{sqlite} [7] in our implementation.
\begin{description}
\item[\textit{libmandoc}] \hfill \\
\textit{libmandoc} is a library interface to a validating compiler. It provides
interface to parse and build an AST (Abstract Syntax Tree) of the man page, 
and interface for traversing that tree in order to extract the data from nodes
which are of our interest.
\end{description}
\begin{description}
\item[\textit{sqlite}] \hfill \\
\textit{sqlite} is an embedded relational database management system providing a
relatively small and easy to use C library interface. One of the main reason
for choosing it over the myriad of other possible options was that it provides
in built support for full text search through it's FTS virtual table module [8].
The FTS module can be accessed using pretty much standard SQL syntax, and it is
still flexible enough to allow us to implement our own ranking function as
per our needs. Besides that we have been able to utilize the RDBMS support of
\textit{Sqlite} to store additional metadata in the form of normal database
tables without any hassles.
\end{description}
\section{Implementation Details}
Due to space constraints we cannot go into enough implementation details in this
abstract but we would like to talk a bit about some important components of this
project:
\begin{description}
\item[makemandb(1)] \hfill \\
\textit{makemandb(1)} [9] is the key component of this implementation. It
traverses the filesystem, reads the raw man page source files, feeds them to them
\textit{libmandoc} and then stores the extracted data in the database using
\textit{sqlite}.
\end{description}
\begin{description}
\item[apropos(1)] \hfill \\
This is the version of \textit{apropos(1)} written from scratch utilizing the
full text search functionality of \textit{sqlite}. Unlike the classical version
of \textit{apropos(1)} it only displays the top 10 results relevant to the user
query and most of the times this is sufficient as we shall see later. Also, it
shows a brief snippet for each of the search results, making it more easy to
find out the relevant documents.
\end{description}
\begin{description}
\item[apropos-utils(3)] \hfill \\
\textit{apropos-utils(3)} [10] is a small library interface provided with this
implementation.
It provides functions for querying the FTS index and processing the results in
a user supplied callback function. It's main purpose is to develop different
interfaces on top of this implementation for different use cases. For example we
have built a small CGI application using it for doing the searches from a web
browser, similarly we also built an IRC bot using this 
\end{description}
\section{Results}
We would like to show how our implementation solves the problems cited earlier
with the classical version of \textit{apropos(1)}.
\footnote{Although this implementation of \textit{apropos(1)} returns 10 results
in normal case for a query but in the following listings we have snipped the
results to save space
}
\lstset{language = sh, caption={Add new user},}
\begin{lstlisting}
$ \textit{apropos(1)} ``add new user''
ssh-add(1)      adds private key identities to the authentication agent
...on the command line. If any file requires a passphrase, ssh-add
asks for the passphrase from the user. The passphrase is read from the
user's tty. ssh-add retries the last passphrase if multiple identity
files are given...

chpass(1)       add or change user database information
add or change user database information

useradd(8)      add a user to the system
The useradd utility adds a user to the system, creating and populating
a home directory if necessary. Any skeleton files will be provided for
the new user if they exist in the skel-dir directory (see the k
option). Default...
.
.
.
\end{lstlisting}
\lstset{language = sh, caption={make directory},}
\begin{lstlisting}
$ \textit{apropos(1)} ``make directory''
make(1) maintain program dependencies
...CURDIR A path to the directory where make was executed. Refer to
the description of PWD for more details. MAKE The name that make was
executed with argv[0] . For compatibility make also sets .MAKE with
the same value. The...

mkdir(1)        make directories
make directories

ln(1)   make links
...a directory in which to place the link; otherwise it is placed in
the current directory. If only the directory is specified, the link
will be made to the last component of source_file . Given more than
two arguments, ln makes...

mkfifo(1)       make fifos
make fifos...of a=rw mkfifo requires write permission in the parent
directory. mkfifo exits 0 if successful, and >0 if an...

mkdir(2)        make a directory file
...will contain the directory has been exhausted. EDQUOT The user's
quota of inodes on the file system on which the directory is being
created has been exhausted. EIO An I/O error occurred while making the
directory entry or...
\end{lstlisting}
\lstset{language = sh, caption={get process status},}
\begin{lstlisting}
$ \textit{apropos(1)} ``get process status''
ps(1)   process status
process status

netstat(1)      show network status
...use the fstat(1) command to find out which process or processes
hold references to a socket. The interface display...show network
status

bounce(8)       Postfix delivery status reports
...the master(8) process manager.  The bounce(8) daemon
processes two types of service requests: Append a recipient
(non-)delivery status record to a per message log file. Enqueue a
delivery status notification message, with a...

ocsp(1) Online Certificate Status Protocol utility
Online Certificate Status Protocol utility...it is in client mode. The
request(s) the responder processes can be either specified on the
command line (using...

fstat(1)        display status of open files
...the owner of the process (effective UID). CMD The command name of
the process. PID The process ID. FD The...display status of open files
\end{lstlisting}

\begin{figure}[htp]
\includegraphics[scale=0.30]{/home/abhinav/development/AsiaBSDCon/spell.png}
\caption{The spell corrector and the web interface in action}
\label{}
\end{figure}
\section{Related Work}
There are at least two projects which are related to this in some way.
\begin{description}
\item[man-db] \hfill \\
\textit{man-db} [11] is a complete implementation of the man page documentation
system and it is used on a number of GNU/Linux distributions.\textit{man-db}
takes an interesting approach for indexing the man page data. Unlike the
classical \textit{apropos(1)}, it uses a Berkley DB database but still it's index
is limited to the NAME section only. It adds an option `K' to man(1) to allow a
crude full text search but it is not very efficient nor effective.
\end{description}
\begin{description}
\item[mandocdb] \hfill \\
\textit{mandocdb} [12] is more in line with the goals of our project but it takes
a novel approach. It indexes the keywords extracted from the man pages in a
key-value store using btree(3) [13]. It also comes with it's own implementation
of \textit{apropos(1)} which performs search using this key-value store. The
main key point of this implementation is that it exploits the semantic structure
of the man pages. 
\end{description}
\section{Future Work}
\begin{description}
\item[Work on Ranking Algorithm] \hfill \\
We have used a ranking algorithm based on probabilistic model [14] of information
retrieval. It is essentially based on the Okapi BM25F algorithm [15] and uses
certain parameters whose values are usually dependent on the corpus and the
search application. For example we have used certain weights for different
sections of man pages. At the moment these values have been determined manually
but we would like to use some machine learning techniques in the coming days to
automate this.
\end{description}
\begin{description}
\item[Fix Some Loose Ends In Parsing of man pages] \hfill \\
Although the parsing routine is working fine for most purposes on the man pages
supplied with NetBSD and also on most of the man pages found in pkgsrc. But there
are perhaps a few corner cases still to be fixed. Besides that another issue that
is to be addressed is the parsing of the escape sequences which are used
extensively in the \textit{man(7)} [16] based man pages. We would like to address
these issues in the coming days.
\end{description}
\section{Acknowledgement}
This project was developed as part of \textbf{Google Summer of Code 2011} [17],
so thanks to Google for sponsoring it. We would also like to thank
\textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
project, he also helped by pointing out several issues in the parsing related
code. We would also like to thank \textbf{David Young} who was involved with
this project closely and offered useful help and guidance. A special thanks goes
to \textbf{Thomas Klausner} who helped in writing and reviewing our man pages.
Thanks to Petra Zedlier for administering the GSoC program for \textit{The NetBSD
Foundation}.
\begin{thebibliography}{20}
\bibitem{1}
\emph{NetBSD manual page for apropos(1)}
\newline http://netbsd.gw.com/cgi-bin/man-cgi?apropos++NetBSD-5.1

\bibitem{2}
\emph{NetBSD manual page for makewhatis(1)}
\newline http://netbsd.gw.com/cgi-bin/man-cgi?makewhatis++NetBSD-5.1

\bibitem{3}
Brin, S.; Page L.
\emph{The Anatomy of a Large-Scale Hypertextual Web Search Engine}
Computer Networks and ISDN Systems
30:107-117, 1998
\bibitem{4}
Manning; Raghwan; Schutze
\emph{Introduction to information retrieval},
3-9,
2008
\bibitem{5}
Frakes; Baeza-Yates
\emph{Information retrieval data structures
\& algorithms},
131-161,
1992

\bibitem{6}
\emph{mdocml online manual page for
libmandoc}
\newline http://mdocml.bsd.lv/mandoc.3.html

\bibitem{7}
\emph{Sqlite home page}
\newline http://sqlite.org

\bibitem{8}
\emph{Sqlite FTS3 and FTS4 Extensions}
\newline  http://sqlite.org/fts3.html

\bibitem{9}
\emph{Online manual page for makemandb(1)}
\newline http://netbsd-soc.sourceforge.net/projects/apropos\_replacement/makemandb.html1

\bibitem{10}
\emph{Online manual page for apropos-utils(3)}
\newline http://netbsd-soc.sourceforge.net/projects/apropos\_replacement/apropos-utils.html3

\bibitem{101}
\emph{man-db, the on-line manual database}
\newline http://man-db.nongnu.org/

\bibitem{12}
\emph{Online manual page for mandocdb(1)}
\newline http://mdocml.bsd.lv/mandocdb.8.html

\bibitem{13}
\emph{NetBSD online manual page for btree(3)}
\newline http://netbsd.gw.com/cgi-bin/man-cgi?btree+3+NetBSD-5.1

\bibitem{14}
Fuhr, Norbert
\emph{Probabilistic models in information
retrieval}
The Computer Journal
1992
\bibitem{15}
Zaragoza H.; Craswell N.; Taylor M.;
Saria S.; Robertson S.
\emph{Microsoft Cambridge at TREC–13: Web
and HARD tracks}
In proceedings of TREC-2004

\bibitem{16}
\emph{Online manual page for man(7)}
\newline http://mdocml.bsd.lv/man.7.html

\bibitem{17}
\emph{Google Summer of Code home page}
\newline http://code.google.com/soc/

\bibitem{18}
\emph {The mdocml project home page}
\newline http://mdocml.bsd.lv
\end{thebibliography}
\end{document}

### 2011-12-25 paper.tex
Fix a duplication

@@
 In this paper we discuss the limitations of the traditional implementation of
-\textit{\textit{\textit{apropos(1)}(1)}}, how did we solve those limitations in our implementation
+\textit{apropos(1)}, how did we solve those limitations in our implementation
 and what other modern implementations are available out there

### 2011-12-25 paper.tex
Convert instances of apropos(1) to apropos and change some active voice to passive voice. More work coming.

@@
 \author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
-Joerg Sonnenberger $<$joerg@netbsd.org$>$}
+Joerg Sonnenberger $<$joerg@NetBSD.org$>$}
 \begin{document}
@@
 \section{Abstract}
-Unix like operating systems have withstood the test of time for 50 odd years for
-several technical and philosophical reasons and one of those reasons is the
+Unix like operating systems have withstood the test of time for 40 odd years for
+several technical and philosophical reasons. One of those reasons is the
 quality documentation they ship in the form of man pages. They are a single point
@@
 
-Traditionally \textit{apropos(1)} [1] has been there to act as a search
-interface but to a
-large extent it hasn't really lived up to it's expectation. \textit{\textit{apropos(1)}} was
+Traditionally \textit{apropos} [1] has been there to act as a search
+interface but to a large extent it hasn't really lived up to it's expectation.
+\textit{apropos} was
 developed in the early days of Unix when computing resources were scarce and
-therefore we believe it was the primary reason that it's design was kept so
+which was the primary reason that it's design was kept so
 minimal and simple.
 
-In this paper we discuss the limitations of the traditional implementation of
-\textit{apropos(1)}, how did we solve those limitations in our implementation
-and what other modern implementations are available out there
-our own implementation.
+In this paper the limitations of the traditional implementation of
+\textit{apropos} are discussed along with brief details of how those limitations
+were solved in this implementation and also what other modern implementations
+are available out there.
 \section{Introduction}
-The classical version of \textit{apropos(1)} has been implemented by simply
+The classical version of \textit{apropos} has been implemented by simply
 indexing the keywords in the NAME section of the man pages in a plain text file
@@
 
-This simplified design of \textit{apropos(1)} resulted in limited utility and usability.
-The searches are limited to the keywords in the NAME section of the keywords. If
+This simplified design of \textit{apropos(1)} resulted in limited utility and
+usability.The searches are limited to the keywords in the NAME section of the
+ keywords. If
 only a user knows the exact keywords he gets the right results otherwise most of
@@
 makes perfect sense that we leverage the advancement in technology to solve the
-problem of an effective man page search tool. In present time we have
-powerful machines capable of running the search algorithms efficiently and disk
-space is cheap enough that we can afford to index additional metadata from man
-pages, which are a necessary prerequisite for an effective search tool.
+problem of an effective man page search tool, considering the fact that the man
+pages consist of structured data.
+
+In present times the machines are powerful and  capable of running the search
+algorithms efficiently. Disk
+space is also cheap enough that indexing of additional metadata from man pages
+can be easily afforded. These are necessary prerequisites for building an
+effective search tool.
 
 \section{Limitations of Conventional \textit{apropos(1)}}
-In this section we will see results of some sample query searches from
-the classical version of \textit{apropos(1)} and analyze its shortcomings.
+In this section results of some sample query searches from
+the classical version of \textit{apropos} are shown and their shortcomings are
+analyzed.
 
 \subsection{Lack of support for free form queries}
-The conventional \textit{apropos(1)} is limited to the keywords used in the NAME section
-of the man pages. If the user specifies keywords relevant to the page that he
-is looking but probably not used in it's NAME section, \textit{apropos(1)} would not return
+The conventional \textit{apropos} is limited to the keywords used in the NAME
+section
+of the man pages. If the user specifies keywords relevant to the page which he
+is looking but probably those keywords are not used in it's NAME section,
+then \textit{apropos(1)} would not return
 anything relevant. So in essence the user cannot use free form queries like
-supported by modern search applications.
+those supported by modern search applications.
 \lstset{language = sh, caption={No results for free form queries}}
 \begin{lstlisting}
-$ \textit{apropos(1)} ``add new user''
-adding new user: nothing appropriate
+$ apropos(1) ``add new user''
+add new user: nothing appropriate
 
-$ \textit{apropos(1)} ``get process status''
+$ apropos(1) ``get process status''
 get process status: nothing appropriate
 
-$ \textit{apropos(1)} ``termcap database''
+$ apropos(1) ``termcap database''
 termcap database: nothing appropriate
 
-$ \textit{apropos(1)} ``signal number to string''
+$ apropos(1) ``signal number to string''
 signal number to string: nothing appropriate
@@
 \subsection{Lack of basic language support}
-Another major limitation of the classical version of \textit{apropos(1)} is that
+Another major limitation of the classical version of \textit{apropos} is that
 it has no
-natural language support. For example in the following listing we can see that
-while \textit{apropos(1)} returns the correct result for the query \textit{``make directories''} but it fails when we use the keyword \textit{``directory''}
-in place of \textit{``directories''} although the two words are based on same
-root word.
+natural language support. For example in the following listing it can be seen
+that while \textit{apropos} returns the correct result for the query \textit{``make directories''} but it fails when the keyword \textit{``directory''} is
+used in place of \textit{``directories''}, although the two words are based on
+same root word.
 \lstset{language = sh, caption={No support for stems or word with same roots},}
 \begin{lstlisting}
-$ \textit{apropos(1)} ``make directories''
+$ apropos ``make directories''
 mkdir (1) - make directories
-$ \textit{apropos(1)} ``make directory''
+$ apropos ``make directory''
 make directory: nothing appropriate
 
-$ \textit{apropos(1)} "upgrading software package"
+$ apropos "upgrading software package"
 pkg_add (1) - a utility for installing and upgrading software package
 distributions
-$ \textit{apropos(1)} "upgrading software packages"
+$ apropos "upgrading software packages"
 upgrading software packages: nothing appropriate
@@
 
-Similarly, it is very common for users to misspell keywords in a query and the
-classical \textit{apropos(1)} has no support for it either.
+Similarly, it is very common for users to misspell keywords in a query and \textit{apropos} has no support for it either.
 \lstset{language = sh, caption={No spelling correction},}
 \begin{lstlisting}
-$ \textit{apropos(1)} ``copy strings''
+$ apropos ``copy strings''
 stpcpy, stpncpy, strcpy, strncpy (3) - copy strings
-$ \textit{apropos(1)} ``coppy strings''
+$ apropos ``coppy strings''
 coppy strings: nothing appropriate
@@
 \subsection{Unintelligible Output}
-Because the way \textit{apropos(1)} works, sometimes it's output can be unintelligible and
-it can be very hard to find the results which are relevant to the user.
+Because of the way \textit{apropos} works, sometimes it's output can be
+unintelligible and it can be very hard for the user to identify the results which
+are relevant to him.
 \lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},}
@@
 are stored on the filesystem in the from of hard (or soft) links and these
-have to be mentioned in the makefiles explicitly using the MKLINK flag. This
-approach works fine but we feel it is a mess from maintenance point of view.
-When \textit{apropos(1)} maintains an index of the man page metadata then it
-should be possible to fix this mess by utilizing that index. But yet again, the
-simplistic implementation of \textit{apropos(1)} does not leave any room for
+have to be mentioned in the makefiles explicitly using the MLINKS mechanism. This
+approach works fine but it is a mess from maintenance point of view.
+It should be possible to fix this by utilizing the index already built and
+maintained by \textit{apropos} and related tools, but yet again, the
+simplistic implementation of \textit{apropos} does not leave any room for
 improvement.
@@
 \section{Proposed Solution}
-We propose a simple and straightforward solution. The idea is to parse and index
+A very simple and straightforward solution is proposed to solve these problems.
+The idea is to parse and index
 the complete content (or at least most of the content) in the form of an
-inverted index {4} and use it to build a full text search
+inverted index [4] and use it to build a full text search
 interface. Having an index based on the complete content of the man pages solves
@@
 For example queries like \textit{``installing new software package''}
-will get you the results.
+will now get results.
 \end{description}
@@
 When parsing the man pages and building the index, it is also possible to
-pre-process the tokens extracted from the man page to support some of the
-basic natural language processing functionalities. We have used stemming [5] to
+pre-process the tokens extracted from the man pages to support some of the very
+basic natural language processing functionalities. In this implementation the
+Porter stemming algorithm [5] has been used to
 reduce the individual tokens extracted from the man pages to their root words.
@@
 
-Similarly along with the inverted index, we can also build a dictionary of the
-keywords frequently occurring in the corpus of man pages and use it to support
-spelling correction.
+Similarly along with the inverted index, a dictionary of the keywords frequently
+occurring in the corpus of man pages can also be built and used to support
+spelling suggestion.
 
-We have used both word stemming and spelling correction in our implementation to
-make the search experience more smooth.
+In this implementation, both word stemming and spelling correction in our implementation are used to make the search experience more smooth.
 \end{description}
@@
 \item[Bookkeeping of man page metadata] \hfill \\
-In our implementation we have gone ahead and also indexed additional metadata
+In this implementation we have gone ahead and also indexed additional metadata
 related to the man pages, for example we are indexing an md5 hash of the man
@@
 \begin{lstlisting}
-$ \textit{apropos(1)} ``add new user''
+$ apropos ``add new user''
 ssh-add(1)      adds private key identities to the authentication agent
@@
 \begin{lstlisting}
-$ \textit{apropos(1)} ``make directory''
+$ apropos ``make directory''
 make(1) maintain program dependencies
@@
 \begin{lstlisting}
-$ \textit{apropos(1)} ``get process status''
+$ apropos ``get process status''
 ps(1)   process status
@@
 to \textbf{Thomas Klausner} who helped in writing and reviewing our man pages.
-Thanks to Petra Zedlier for administering the GSoC program for \textit{The NetBSD
+Thanks to Petra Zeidler for administering the GSoC program for \textit{The NetBSD
 Foundation}.
@@
 \bibitem{5}
-Frakes; Baeza-Yates
-\emph{Information retrieval data structures
-\& algorithms},
-131-161,
-1992
+Porter, M. F.
+\emph{An algorithm for suffix stripping},
+Program,
+14(3): 130-137,
+1980
 

### 2011-12-25 paper.tex
More conversion from active to passive.

@@
 reduce the individual tokens extracted from the man pages to their root words.
-This allows us to support more flexible searches. For example both
+This enables support for more flexible searches. For example both
 \textit{``Installing new packages''} and \textit{``install new package''} will
@@
 \item[Bookkeeping of man page metadata] \hfill \\
-In this implementation we have gone ahead and also indexed additional metadata
-related to the man pages, for example we are indexing an md5 hash of the man
-page, the device id, inode number and modification time of the man page file so
-as to support incremental updating of the index as new man pages are installed
-or the old ones are modified/updated.
+In this implementation additional metadata related to the man pages, for example
+an md5 hash, the device id, inode number and modification time
+of the man page file etc. are indexed and stored so
+as to support fast and hassle free updating of the index as new man pages are
+installed or the old ones are modified/updated.
 
-Similarly we are also maintaining a separate index of all the aliases of a man
-page. This will allow us to get rid of all the hard or symbolic links of the man
-pages which are scattered throughout the filesystem, and also help in getting rid
-of the MKLINK flags in the makefiles.
+Similarly a separate index of all the man page aliases is stored and maintained.
+This provides an option to get rid of all the hard or symbolic links of the man
+pages scattered throughout the filesystem, and also for clean up of the MLINKS
+mess in the makefiles.
 \end{description}
 \subsection{Tools Used}
-The two main tasks that we needed to perform were parsing of the man pages and
-building an index of the data, and to do these tasks we have used \textit{libmandoc} [6]
-and \textit{sqlite} [7] in our implementation.
+The two main tasks that are needed to be performed are parsing of the man pages
+and building an index of the data. \textit{libmandoc} [6]
+and \textit{sqlite} [7] have been used for the two tasks respectively in this
+implementation.
 \begin{description}
@@
 relatively small and easy to use C library interface. One of the main reason
-for choosing it over the myriad of other possible options was that it provides
+for choosing it over the myriad of other possible options is that it provides
 in built support for full text search through it's FTS virtual table module [8].
 The FTS module can be accessed using pretty much standard SQL syntax, and it is
-still flexible enough to allow us to implement our own ranking function as
-per our needs. Besides that we have been able to utilize the RDBMS support of
-\textit{Sqlite} to store additional metadata in the form of normal database
-tables without any hassles.
+still flexible enough to accept user supplied ranking function to suit the needs
+of the application. Besides that another advantage of \textit{sqlite} is the
+RDBMS support which makes it very easy to store additional metadata in the form
+of normal database tables without any hassles.
 \end{description}
 \section{Implementation Details}
-Due to space constraints we cannot go into enough implementation details in this
-abstract but we would like to talk a bit about some important components of this
-project:
+Due to space constraints it is not possibile to go into enough implementation details but in this section some important components of this project are
+discussed in brief.
 \begin{description}
-\item[makemandb(1)] \hfill \\
-\textit{makemandb(1)} [9] is the key component of this implementation. It
-traverses the filesystem, reads the raw man page source files, feeds them to them
-\textit{libmandoc} and then stores the extracted data in the database using
-\textit{sqlite}.
+\item[makemandb] \hfill \\
+\textit{makemandb} [9] is the key component of this implementation. It is a
+command line tool which
+traverses the filesystem, reads the raw man page source files, feeds them to the
+\textit{libmandoc} parser and then stores the extracted data in the database
+using \textit{sqlite}.
 \end{description}
 \begin{description}
-\item[apropos(1)] \hfill \\
-This is the version of \textit{apropos(1)} written from scratch utilizing the
+\item[apropos] \hfill \\
+This is the version of \textit{apropos} written from scratch utilizing the
 full text search functionality of \textit{sqlite}. Unlike the classical version
-of \textit{apropos(1)} it only displays the top 10 results relevant to the user
-query and most of the times this is sufficient as we shall see later. Also, it
+of \textit{apropos}, it only displays the top 10 results relevant to the user
+query and most of the times this is sufficient as will be seen later. Also, it
 shows a brief snippet for each of the search results, making it more easy to
-find out the relevant documents.
+identify the relevant documents.
 \end{description}
 \begin{description}
-\item[apropos-utils(3)] \hfill \\
-\textit{apropos-utils(3)} [10] is a small library interface provided with this
-implementation.
-It provides functions for querying the FTS index and processing the results in
-a user supplied callback function. It's main purpose is to develop different
-interfaces on top of this implementation for different use cases. For example we
-have built a small CGI application using it for doing the searches from a web
-browser, similarly we also built an IRC bot using this 
+\item[apropos-utils] \hfill \\
+\textit{apropos-utils} [10] is a small library interface provided with this
+implementation. It provides functions for querying the FTS index and for
+processing the results in a user supplied callback function. It's main purpose
+is to develop different interfaces on top of this implementation for different
+use cases. For example a small CGI application was built using it for doing
+the searches from a web browser, similarly an IRC bot was also developed utilizing this interface.
 \end{description}
 \section{Results}
-We would like to show how our implementation solves the problems cited earlier
-with the classical version of \textit{apropos(1)}.
+This section shows results of some of the sample queries on the version of
+developed as part of this project
+\textit{apropos} to demonstrate how it solves many of the problems cited earlier
+with the classical version of \textit{apropos}.
 \footnote{Although this implementation of \textit{apropos(1)} returns 10 results
-in normal case for a query but in the following listings we have snipped the
-results to save space
+in normal case for a query but in the following listings the output has been
+snipped to save space
 }
@@
 \end{lstlisting}
-\lstset{language = sh, caption={get process status},}
+\lstset{language = sh, caption={signal number to string},}
 \begin{lstlisting}
-$ apropos ``get process status''
-ps(1)   process status
-process status
+$ apropos ``signal number to string''
+psignal(3)      system signal messages
+...the signal number is not recognized sigaction(2) , the string
+Unknown signal is produced. The psiginfo function produces the same
+output as the psignal function, only it uses the signal number
+information from the si argument. The message strings can...
 
-netstat(1)      show network status
-...use the fstat(1) command to find out which process or processes
-hold references to a socket. The interface display...show network
-status
+intro(2)        introduction to system calls and error numbers
+...undefined signal to a signal(3) or kill(2) function). 23 ENFILE Too
+many open files in system . Maximum number...shell. Pathname A path
+name is a NUL -terminated character string starting with an optional
+slash \&/ , followed by zero or...
 
-bounce(8)       Postfix delivery status reports
-...the master(8) process manager.  The bounce(8) daemon
-processes two types of service requests: Append a recipient
-(non-)delivery status record to a per message log file. Enqueue a
-delivery status notification message, with a...
-
-ocsp(1) Online Certificate Status Protocol utility
-Online Certificate Status Protocol utility...it is in client mode. The
-request(s) the responder processes can be either specified on the
-command line (using...
-
-fstat(1)        display status of open files
-...the owner of the process (effective UID). CMD The command name of
-the process. PID The process ID. FD The...display status of open files
+groff_mdoc(7)   reference for groff's mdoc implementation
+...Qq .Qq string ) , string ) , .Qq string Ns ), string ), .Sq .Sq
+string string .Em or...UNTITLED is used. The section number may be a
+number in the range 1...2, 3 and 9 error \&.\e"     and signal
+handling only. \&.\e" .Sh ERRORS \&.\e...
 \end{lstlisting}
@@
 takes an interesting approach for indexing the man page data. Unlike the
-classical \textit{apropos(1)}, it uses a Berkley DB database but still it's index
+classical \textit{apropos}, it uses a Berkley DB database but still it's index
 is limited to the NAME section only. It adds an option `K' to man(1) to allow a
@@
 key-value store using btree(3) [13]. It also comes with it's own implementation
-of \textit{apropos(1)} which performs search using this key-value store. The
+of \textit{apropos} which performs search using this key-value store. The
 main key point of this implementation is that it exploits the semantic structure
@@
 \item[Work on Ranking Algorithm] \hfill \\
-We have used a ranking algorithm based on probabilistic model [14] of information
-retrieval. It is essentially based on the Okapi BM25F algorithm [15] and uses
-certain parameters whose values are usually dependent on the corpus and the
-search application. For example we have used certain weights for different
-sections of man pages. At the moment these values have been determined manually
-but we would like to use some machine learning techniques in the coming days to
-automate this.
+A ranking algorithm based on probabilistic model [14] of information
+retrieval has been implemented to filter out the most relevant results and show
+them at the top. It is essentially based on the Okapi BM25F algorithm [15] and
+uses certain parameters whose values are usually dependent on the corpus and the
+search application. For example certain weight parameters are assigned to different sections of man pages. At the moment these values have been determined
+manually but one goal is to use some machine learning techniques in the coming
+days to automate this.
 \end{description}
@@
 Although the parsing routine is working fine for most purposes on the man pages
-supplied with NetBSD and also on most of the man pages found in pkgsrc. But there
+supplied with NetBSD and also on most of the man pages found in Pkgsrc. But there
 are perhaps a few corner cases still to be fixed. Besides that another issue that
 is to be addressed is the parsing of the escape sequences which are used
-extensively in the \textit{man(7)} [16] based man pages. We would like to address
-these issues in the coming days.
+extensively in the \textit{man(7)} [16] based man pages. These issues are to be
+addressed in the coming days.
 \end{description}
 \section{Acknowledgement}
-This project was developed as part of \textbf{Google Summer of Code 2011} [17],
-so thanks to Google for sponsoring it. We would also like to thank
+This project has been developed as part of \textbf{Google Summer of Code 2011}
+[17], so thanks to \textbf{Google} for sponsoring it. Special thanks to
 \textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
 project, he also helped by pointing out several issues in the parsing related
-code. We would also like to thank \textbf{David Young} who was involved with
-this project closely and offered useful help and guidance. A special thanks goes
-to \textbf{Thomas Klausner} who helped in writing and reviewing our man pages.
-Thanks to Petra Zeidler for administering the GSoC program for \textit{The NetBSD
-Foundation}.
+code. We would like to thank \textbf{David Young} who was involved with
+this project closely and offered useful help and guidance throughout. A special
+thanks goes to \textbf{Thomas Klausner} who helped in writing and reviewing our
+man pages. Thanks to \textbf{Petra Zeidler} for administering the GSoC program
+for \textit{The NetBSD Foundation}.
 \begin{thebibliography}{20}

### 2011-12-26 paper.tex
Clarify

@@
 \title{Apropos Replacement \newline
-(Extended  Abstract)}
+(Initial Outline)}
 \author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
@@
 developed in the early days of Unix when computing resources were scarce and
-which was the primary reason that it's design was kept so
+which is the primary reason that it's design was kept so
 minimal and simple.
@@
 \textit{apropos} are discussed along with brief details of how those limitations
-were solved in this implementation and also what other modern implementations
-are available out there.
+have been solved in the implementation developed as part of this project and also
+what other modern implementations are available out there.
 \section{Introduction}

### 2011-12-26 paper.tex
more fixes

@@
 probably lack of computing resources in the early days. The plain text file
-consisting of keywords would hardly take few hundreds of kilo bytes of disk space
+consisting of keywords hardly takes few hundreds of kilo bytes of disk space
 and performing search on a plain text file is also not very hard.
@@
 computing world where hard problems like searching the World Wide Web have been
-solved [3] to sufficient degree where most of the data is unstructured, then it
-makes perfect sense that we leverage the advancement in technology to solve the
-problem of an effective man page search tool, considering the fact that the man
-pages consist of structured data.
+solved [3] to sufficient degree, then it makes perfect sense that we leverage the advancement in technology to solve the problem of an effective man page
+search tool, considering the fact that the man
+pages consist of structured data, making the problem somewhat less complex.
 
@@
 of the man pages. If the user specifies keywords relevant to the page which he
-is looking but probably those keywords are not used in it's NAME section,
-then \textit{apropos(1)} would not return
+is looking but probably those keywords are not used in the NAME section,
+then \textit{apropos} would not return
 anything relevant. So in essence the user cannot use free form queries like
@@
 \begin{lstlisting}
-$ apropos(1) ``add new user''
+$ apropos ``add new user''
 add new user: nothing appropriate
 
-$ apropos(1) ``get process status''
+$ apropos ``get process status''
 get process status: nothing appropriate
 
-$ apropos(1) ``termcap database''
+$ apropos ``termcap database''
 termcap database: nothing appropriate
 
-$ apropos(1) ``signal number to string''
+$ apropos ``signal number to string''
 signal number to string: nothing appropriate
@@
 \section{Proposed Solution}
-A very simple and straightforward solution is proposed to solve these problems.
+A very simple and straightforward solution is proposed to solve these problems as
+part of this project.
 The idea is to parse and index
@@
 an md5 hash, the device id, inode number and modification time
-of the man page file etc. are indexed and stored so
-as to support fast and hassle free updating of the index as new man pages are
+of the man page files are indexed and stored so
+as to support fast and hassle free update of the index as new man pages are
 installed or the old ones are modified/updated.
@@
 \subsection{Tools Used}
-The two main tasks that are needed to be performed are parsing of the man pages
+The two main tasks that are needed to be performed to implement this project are
+parsing of the man pages
 and building an index of the data. \textit{libmandoc} [6]

### 2011-12-26 paper.tex
Grammatical fixes

@@
 several technical and philosophical reasons. One of those reasons is the
-quality documentation they ship in the form of man pages. They are a single point
-source of consultation for most of our routine work. But there has been a lack of
-good search tool to accompany this documentation which would increase their
+quality documentation they ship in the form of man pages, which are a single
+source of consultation for most of our routine work. However, so far, there has been a lack of
+good search tool to accompany this documentation, which would increase their
 usefulness manifolds.
 
-Traditionally \textit{apropos} [1] has been there to act as a search
+Traditionally, \textit{apropos} [1] has been there to act as a search
 interface but to a large extent it hasn't really lived up to it's expectation.
@@
 developed in the early days of Unix when computing resources were scarce and
-which is the primary reason that it's design was kept so
-minimal and simple.
+that is the primary reason for its minimalistic and simple design.
 
-In this paper the limitations of the traditional implementation of
-\textit{apropos} are discussed along with brief details of how those limitations
-have been solved in the implementation developed as part of this project and also
-what other modern implementations are available out there.
+In this paper, the limitations of the traditional implementation of
+\textit{apropos} are discussed along with brief details of how these were overcome as part of this.
+Additionally, we compare and contrast our approach with other modern implementations available out there.
+
 \section{Introduction}
@@
 consisting of keywords hardly takes few hundreds of kilo bytes of disk space
-and performing search on a plain text file is also not very hard.
+and performing search on a plain text file is quite easy.
 
 This simplified design of \textit{apropos(1)} resulted in limited utility and
-usability.The searches are limited to the keywords in the NAME section of the
- keywords. If
-only a user knows the exact keywords he gets the right results otherwise most of
-the times the searches are full of bogus results or a dead end. In the modern
+usability as the searches are limited to the keywords in the NAME section of the
+ keywords. Only if
+a user knows the exact keywords do they get the appropriate results; otherwise most of
+the times the searches are full of irrelavant results or possibly a dead end. In the modern
 computing world where hard problems like searching the World Wide Web have been
-solved [3] to sufficient degree, then it makes perfect sense that we leverage the advancement in technology to solve the problem of an effective man page
-search tool, considering the fact that the man
+solved [3] to a sufficient degree, it makes perfect sense to leverage the advancement in technology 
+in order to solve the problem. This problem is made even simpler considering that the man
 pages consist of structured data, making the problem somewhat less complex.
 
-In present times the machines are powerful and  capable of running the search
+In present times, the machines are powerful and  capable of running the search
 algorithms efficiently. Disk
-space is also cheap enough that indexing of additional metadata from man pages
+space is also sufficiently cheap that any extra space incurred by indexing of additional metadata from man pages
 can be easily afforded. These are necessary prerequisites for building an
@@
 of the man pages. If the user specifies keywords relevant to the page which he
-is looking but probably those keywords are not used in the NAME section,
+is looking but if those keywords are not used in the NAME section,
 then \textit{apropos} would not return
-anything relevant. So in essence the user cannot use free form queries like
+anything relevant. So, in essence, the user cannot use free form queries like
 those supported by modern search applications.
@@
 natural language support. For example in the following listing it can be seen
-that while \textit{apropos} returns the correct result for the query \textit{``make directories''} but it fails when the keyword \textit{``directory''} is
-used in place of \textit{``directories''}, although the two words are based on
+that while \textit{apropos} returns the correct result for the query \textit{``make directories''}, it fails when the keyword \textit{``directory''} is
+used in place of \textit{``directories''} even though the two words are based on
 same root word.
@@
 Because of the way \textit{apropos} works, sometimes it's output can be
-unintelligible and it can be very hard for the user to identify the results which
-are relevant to him.
+unintelligible and it can be very hard for the user to identify relevant results.
+
 \lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},}
@@
 are no longer limited to the keywords defined in the NAME section of the man
-pages, the keywords used throughout the body of the page also play a role.
-For example queries like \textit{``installing new software package''}
-will now get results.
+pages as the keywords used throughout the body of the page also play a role.
+e.g. queries like \textit{``installing new software package''}
+will now produce relevant results.
 \end{description}
@@
 pre-process the tokens extracted from the man pages to support some of the very
-basic natural language processing functionalities. In this implementation the
+basic natural language processing functionalities. In this implementation, the
 Porter stemming algorithm [5] has been used to
@@
 parsing of the man pages
-and building an index of the data. \textit{libmandoc} [6]
-and \textit{sqlite} [7] have been used for the two tasks respectively in this
-implementation.
+and building an index from the data. We have used \textit{libmandoc} [6]
+and \textit{sqlite} [7] have for these the two tasks.
 \begin{description}
@@
 \textit{libmandoc} is a library interface to a validating compiler. It provides
-interface to parse and build an AST (Abstract Syntax Tree) of the man page, 
-and interface for traversing that tree in order to extract the data from nodes
+interface to parse and build an AST (Abstract Syntax Tree) of the man page. It also provides
+an interface for traversing that tree in order to extract the data from nodes
 which are of our interest.
@@
 \section{Implementation Details}
-Due to space constraints it is not possibile to go into enough implementation details but in this section some important components of this project are
-discussed in brief.
+Due to space constraints it is not possibile to go into enough implementation details, we discuss 
+the most important components of this project  in the section below:
 \begin{description}

### 2011-12-26 paper.tex
Minor fixes

@@
 }
-\title{Apropos Replacement \newline
+\title{Apropos Replacement: Development of a full text search tool for man pages \newline
 (Initial Outline)}
@@
 In this paper, the limitations of the traditional implementation of
-\textit{apropos} are discussed along with brief details of how these were overcome as part of this.
+\textit{apropos} are discussed along with brief details of how these were overcome as part of this project.
 Additionally, we compare and contrast our approach with other modern implementations available out there.
@@
 
-This simplified design of \textit{apropos(1)} resulted in limited utility and
-usability as the searches are limited to the keywords in the NAME section of the
- keywords. Only if
-a user knows the exact keywords do they get the appropriate results; otherwise most of
-the times the searches are full of irrelavant results or possibly a dead end. In the modern
+This simplified design of \textit{apropos} resulted in limited utility and
+usability as the searches are limited to the keywords defined in the NAME
+section of the man pages. Only if a user knows the exact keywords do they get
+the appropriate results; otherwise most of
+the times the searches are full of irrelevant results or possibly a dead end. In the modern
 computing world where hard problems like searching the World Wide Web have been
-solved [3] to a sufficient degree, it makes perfect sense to leverage the advancement in technology 
-in order to solve the problem. This problem is made even simpler considering that the man
-pages consist of structured data, making the problem somewhat less complex.
+solved [3] to a sufficient degree, it makes perfect sense to leverage the
+advancement in technology in order to solve the problem. This problem is made
+even simpler considering that the man pages consist of structured data.
 
@@
 algorithms efficiently. Disk
-space is also sufficiently cheap that any extra space incurred by indexing of additional metadata from man pages
+space is also sufficiently cheap that any extra space incurred by indexing of
+additional metadata from man pages
 can be easily afforded. These are necessary prerequisites for building an
@@
 
-\section{Limitations of Conventional \textit{apropos(1)}}
+\section{Limitations of Conventional \textit{apropos}}
 In this section results of some sample query searches from
@@
 \subsection{Lack of support for free form queries}
-The conventional \textit{apropos} is limited to the keywords used in the NAME
-section
-of the man pages. If the user specifies keywords relevant to the page which he
-is looking but if those keywords are not used in the NAME section,
-then \textit{apropos} would not return
-anything relevant. So, in essence, the user cannot use free form queries like
-those supported by modern search applications.
+As noted earlier the conventional \textit{apropos} is limited to the keywords
+used in the NAME section of the man pages. This means that the users do not have
+a whole lot of choice for specifying keywords in their queries. Besides they
+cannot search for keywords which are not usually specified in the title of a man
+page, for example a query like ``EINVAL'' would return no results.
 \lstset{language = sh, caption={No results for free form queries}}
@@
 Another major limitation of the classical version of \textit{apropos} is that
-it has no
-natural language support. For example in the following listing it can be seen
-that while \textit{apropos} returns the correct result for the query \textit{``make directories''}, it fails when the keyword \textit{``directory''} is
-used in place of \textit{``directories''} even though the two words are based on
-same root word.
+it is not smart enough to provide basic natural language processing constructs
+like stemming and spelling corrections.
+For example in the following listing it can be seen
+that while \textit{apropos} returns the correct result for the query
+\textit{``make directories''}, it fails when the keyword \textit{``directory''}
+is used in place of \textit{``directories''}, even though the two words are based
+on same root word.
 \lstset{language = sh, caption={No support for stems or word with same roots},}
@@
 It should be possible to fix this by utilizing the index already built and
-maintained by \textit{apropos} and related tools, but yet again, the
-simplistic implementation of \textit{apropos} does not leave any room for
-improvement.
+maintained by \textit{apropos}, but yet again, the simplistic implementation of
+\textit{apropos} does not leave any room for improvement.
 
@@
 The users can express their queries in more natural language form as the searches
-are no longer limited to the keywords defined in the NAME section of the man
-pages as the keywords used throughout the body of the page also play a role.
-e.g. queries like \textit{``installing new software package''}
-will now produce relevant results.
+are no longer limited to the the NAME section.
+For example, queries like \textit{``installing new software package''}
+now produce relevant results.
 \end{description}
@@
 Similarly along with the inverted index, a dictionary of the keywords frequently
-occurring in the corpus of man pages can also be built and used to support
+occurring in the corpus of man pages is also built and used to support
 spelling suggestion.
-
-In this implementation, both word stemming and spelling correction in our implementation are used to make the search experience more smooth.
 \end{description}
@@
 \item[Bookkeeping of man page metadata] \hfill \\
-In this implementation additional metadata related to the man pages, for example
+In this implementation, additional metadata related to the man pages, for example
 an md5 hash, the device id, inode number and modification time
@@
 \subsection{Tools Used}
-The two main tasks that are needed to be performed to implement this project are
-parsing of the man pages
-and building an index from the data. We have used \textit{libmandoc} [6]
-and \textit{sqlite} [7] have for these the two tasks.
+The two main operations that are critical for this project are parsing of the
+man pages and building of an index of the
+data obtained from the parsing process. \textit{libmandoc} [6]
+and \textit{sqlite} [7] have been used for executing these the two tasks.
 \begin{description}
@@
 \textit{libmandoc} is a library interface to a validating compiler. It provides
-interface to parse and build an AST (Abstract Syntax Tree) of the man page. It also provides
-an interface for traversing that tree in order to extract the data from nodes
-which are of our interest.
+interface to parse and build an AST (Abstract Syntax Tree) of the man page. It
+also provides an interface for traversing that tree in order to extract the data
+from nodes which are of our interest.
 \end{description}
@@
 \textit{sqlite} is an embedded relational database management system providing a
-relatively small and easy to use C library interface. One of the main reason
+relatively small and easy to use C library interface. One of the main reasons
 for choosing it over the myriad of other possible options is that it provides
@@
 still flexible enough to accept user supplied ranking function to suit the needs
-of the application. Besides that another advantage of \textit{sqlite} is the
-RDBMS support which makes it very easy to store additional metadata in the form
+of the application. Besides that, another advantage of \textit{sqlite} is the
+RDBMS support, which makes it very easy to store additional metadata in the form
 of normal database tables without any hassles.
@@
 \section{Implementation Details}
-Due to space constraints it is not possibile to go into enough implementation details, we discuss 
-the most important components of this project  in the section below:
+Due to space constraints it is not possible to go into enough implementation
+details, the most important components of this project are described in brief
+in this section.
 \begin{description}
@@
 processing the results in a user supplied callback function. It's main purpose
-is to develop different interfaces on top of this implementation for different
+is to develop different interfaces on top of it for different
 use cases. For example a small CGI application was built using it for doing
@@
 \footnote{Although this implementation of \textit{apropos(1)} returns 10 results
-in normal case for a query but in the following listings the output has been
+in normal cases for a query but in the following listings the output has been
 snipped to save space
@@
 \item[mandocdb] \hfill \\
-\textit{mandocdb} [12] is more in line with the goals of our project but it takes
-a novel approach. It indexes the keywords extracted from the man pages in a
+\textit{mandocdb} [12] is more in line with the goals of this project but it
+takes a novel approach. It indexes the keywords extracted from the man pages in a
 key-value store using btree(3) [13]. It also comes with it's own implementation
@@
 uses certain parameters whose values are usually dependent on the corpus and the
-search application. For example certain weight parameters are assigned to different sections of man pages. At the moment these values have been determined
-manually but one goal is to use some machine learning techniques in the coming
-days to automate this.
+search application. For example certain weight parameters are assigned to
+different sections of man pages. At the moment these values have been determined
+manually but one goal is to use some supervised machine learning techniques in
+the order to automate this.
 \end{description}
@@
 supplied with NetBSD and also on most of the man pages found in Pkgsrc. But there
-are perhaps a few corner cases still to be fixed. Besides that another issue that
+are perhaps a few corner cases still to be fixed. Besides that, another issue
+that
 is to be addressed is the parsing of the escape sequences which are used
@@
 \section{Acknowledgement}
-This project has been developed as part of \textbf{Google Summer of Code 2011}
+This project has been developed as part of \emph{Google Summer of Code 2011}
 [17], so thanks to \textbf{Google} for sponsoring it. Special thanks to
@@
 this project closely and offered useful help and guidance throughout. A special
-thanks goes to \textbf{Thomas Klausner} who helped in writing and reviewing our
-man pages. Thanks to \textbf{Petra Zeidler} for administering the GSoC program
-for \textit{The NetBSD Foundation}.
+thanks goes to \textbf{Thomas Klausner} who helped in writing and reviewing
+man pages for this project. Thanks to \textbf{Petra Zeidler} for administering
+the GSoC program for \textit{The NetBSD Foundation}.
 \begin{thebibliography}{20}
@@
 \bibitem{15}
-Zaragoza H.; Craswell N.; Taylor M.;
-Saria S.; Robertson S.
+Zaragoza, H.; Craswell, N.; Taylor, M.;
+Saria, S.; Robertson, S.
 \emph{Microsoft Cambridge at TREC–13: Web

### 2011-12-26 paper.tex
Improve abstract

@@
 developed in the early days of Unix when computing resources were scarce and
-that is the primary reason for its minimalistic and simple design.
+that is the primary reason for its minimalistic and simple design. The biggest
+limitation of \textit{apropos} is it's limited search capabilities besides
+man others.
 
-In this paper, the limitations of the traditional implementation of
-\textit{apropos} are discussed along with brief details of how these were overcome as part of this project.
-Additionally, we compare and contrast our approach with other modern implementations available out there.
+We worked on fixing this by writing a new implementation of \textit{apropos} As part of \emph{Google Summer of Code 2011} [17]. The main goal of this project was
+the development of a full text search tool for man pages.
+
+In this paper, the limitations of the traditional implementation of apropos
+are discussed along with brief details of how these were overcome as part of
+this project. Additionally, we compare and contrast our approach with other
+modern implementations available out there.
 

### 2012-02-02 apropos_replacement.tex
Fix some typos and rename files.

--- 2011-12-26 paper.tex
@@
 \usepackage{graphicx}
-\usepackage[colorlinks=false]{hyperref}
 \lstset{ %
@@
 Traditionally, \textit{apropos} [1] has been there to act as a search
-interface but to a large extent it hasn't really lived up to it's expectation.
+interface but to a large extent it hasn't really lived up to its expectation.
 \textit{apropos} was
@@
 that is the primary reason for its minimalistic and simple design. The biggest
-limitation of \textit{apropos} is it's limited search capabilities besides
-man others.
+limitation of \textit{apropos} is its limited search capabilities.
 
-We worked on fixing this by writing a new implementation of \textit{apropos} As part of \emph{Google Summer of Code 2011} [17]. The main goal of this project was
-the development of a full text search tool for man pages.
-
-In this paper, the limitations of the traditional implementation of apropos
-are discussed along with brief details of how these were overcome as part of
-this project. Additionally, we compare and contrast our approach with other
-modern implementations available out there.
-
+This paper discusses a new implementation of \textit{apropos} which was done
+as part of \emph{Google Summer of Code 2011} [17]. The goal of this project was
+to replace the conventional apropos in NetBSD with a modern version which
+supports full text searches.
 \section{Introduction}
@@
 This simplified design of \textit{apropos} resulted in limited utility and
-usability as the searches are limited to the keywords defined in the NAME
+usability, as the searches are limited to the keywords defined in the NAME
 section of the man pages. Only if a user knows the exact keywords do they get
 the appropriate results; otherwise most of
-the times the searches are full of irrelevant results or possibly a dead end. In the modern
+the times the searches are full of irrelevant results or possibly a dead end. 
+In the modern
 computing world where hard problems like searching the World Wide Web have been
@@
 effective search tool.
+
+In this paper, the limitations of the traditional implementation of apropos
+are discussed along with brief details of how these were overcome as part of
+this project. Additionally, we compare and contrast our approach with other
+modern implementations available out there.
 
@@
 Another major limitation of the classical version of \textit{apropos} is that
-it is not smart enough to provide basic natural language processing constructs
-like stemming and spelling corrections.
+it is not smart enough to provide basic natural language processing constructs,
+like stemming or spelling corrections.
 For example in the following listing it can be seen
@@
 on same root word.
-\lstset{language = sh, caption={No support for stems or word with same roots},}
+\lstset{language = sh, caption={No support for stems or words with same roots},}
 \begin{lstlisting}
@@
 
-$ apropos "upgrading software package"
+$ apropos ``upgrading software package''
 pkg_add (1) - a utility for installing and upgrading software package
 distributions
-$ apropos "upgrading software packages"
+$ apropos ``upgrading software packages''
 upgrading software packages: nothing appropriate
@@
 \subsection{Unintelligible Output}
-Because of the way \textit{apropos} works, sometimes it's output can be
+Because of the way \textit{apropos} works, sometimes its output can be
 unintelligible and it can be very hard for the user to identify relevant results.
@@
 \begin{lstlisting}
-$ \textit{apropos(1)} power
+$ apropos power
 PCI, pci_activate, pci_bus_devorder, pci_chipset_tag_create,
@@
 pmf_class_network_register, pmf_class_input_register,
-pmf_class_display_register, pmf_system_suspend, pmf_system_resume,
-pmf_system_shutdown, pmf_event_register, pmf_event_deregister,
 pmf_event_inject, pmf_set_platform, pmf_get_platform (9) - power
@@
 the way man pages are handled in NetBSD. The different aliases of the man pages
-are stored on the filesystem in the from of hard (or soft) links and these
+are stored on the file system in the from of hard (or soft) links and these
 have to be mentioned in the makefiles explicitly using the MLINKS mechanism. This
@@
 are no longer limited to the the NAME section.
-For example, queries like \textit{``installing new software package''}
+For example, queries like \textit{``installing new software package''} will
 now produce relevant results.
@@
 data obtained from the parsing process. \textit{libmandoc} [6]
-and \textit{sqlite} [7] have been used for executing these the two tasks.
+and \textit{sqlite} [7] have been used for performing these the two tasks.
 \begin{description}
@@
 also provides an interface for traversing that tree in order to extract the data
-from nodes which are of our interest.
+from its nodes.
 \end{description}
@@
 for choosing it over the myriad of other possible options is that it provides
-in built support for full text search through it's FTS virtual table module [8].
+built in support for full text search through its FTS virtual table module [8].
 The FTS module can be accessed using pretty much standard SQL syntax, and it is
 still flexible enough to accept user supplied ranking function to suit the needs
-of the application. Besides that, another advantage of \textit{sqlite} is the
-RDBMS support, which makes it very easy to store additional metadata in the form
+of the application. Besides that, another advantage of \textit{sqlite} is that, 
+being an RDBMS, it makes it very easy to store additional metadata in the form
 of normal database tables without any hassles.
@@
 query and most of the times this is sufficient as will be seen later. Also, it
-shows a brief snippet for each of the search results, making it more easy to
-identify the relevant documents.
+shows a brief snippet of matching text for each of the search results, making it
+more easy to identify the relevant documents.
 \end{description}
@@
 implementation. It provides functions for querying the FTS index and for
-processing the results in a user supplied callback function. It's main purpose
+processing the results in a user supplied callback function. Its main purpose
 is to develop different interfaces on top of it for different
@@
 with the classical version of \textit{apropos}.
-\footnote{Although this implementation of \textit{apropos(1)} returns 10 results
+\footnote{Although this implementation of \textit{apropos} returns 10 results
 in normal cases for a query but in the following listings the output has been
@@
 $ apropos ``add new user''
-ssh-add(1)      adds private key identities to the authentication agent
-...on the command line. If any file requires a passphrase, ssh-add
-asks for the passphrase from the user. The passphrase is read from the
-user's tty. ssh-add retries the last passphrase if multiple identity
-files are given...
+ssh-add(1)      adds private key identities to the authentication agent...on the command line.
+If any file requires a passphrase, ssh-add asks for the passphrase from the user.
+The passphrase is read from the user's tty.
+ssh-add retries the last passphrase if multiple identity files are given...
 
@@
 useradd(8)      add a user to the system
-The useradd utility adds a user to the system, creating and populating
-a home directory if necessary. Any skeleton files will be provided for
-the new user if they exist in the skel-dir directory (see the k
-option). Default...
+The useradd utility adds a user to the system, creating and populating a home directory if necessary.
+Any skeleton files will be provided for the new user if they exist in the skel-dir directory (see the k option).
+Default...
 .
@@
 make(1) maintain program dependencies
-...CURDIR A path to the directory where make was executed. Refer to
-the description of PWD for more details. MAKE The name that make was
-executed with argv[0] . For compatibility make also sets .MAKE with
-the same value. The...
+...CURDIR A path to the directory where make was executed.
+Refer to the description of PWD for more details.
+MAKE The name that make was executed with argv[0] .
+For compatibility make also sets .MAKE with the same value.
+The...
 
@@
 ln(1)   make links
-...a directory in which to place the link; otherwise it is placed in
-the current directory. If only the directory is specified, the link
-will be made to the last component of source_file . Given more than
-two arguments, ln makes...
+...a directory in which to place the link; otherwise it is placed in the current directory.
+If only the directory is specified, the link will be made to the last component of source_file .
+Given more than two arguments, ln makes...
 
 mkfifo(1)       make fifos
-make fifos...of a=rw mkfifo requires write permission in the parent
-directory. mkfifo exits 0 if successful, and >0 if an...
+make fifos...of a=rw mkfifo requires write permission in the parent directory. mkfifo exits 0 if successful, and >0 if an...
 
 mkdir(2)        make a directory file
-...will contain the directory has been exhausted. EDQUOT The user's
-quota of inodes on the file system on which the directory is being
-created has been exhausted. EIO An I/O error occurred while making the
-directory entry or...
+...will contain the directory has been exhausted.
+EDQUOT The user's quota of inodes on the file system on which the directory is being created has been exhausted.
+EIO An I/O error occurred while making the directory entry or...
 \end{lstlisting}
@@
 psignal(3)      system signal messages
-...the signal number is not recognized sigaction(2) , the string
-Unknown signal is produced. The psiginfo function produces the same
-output as the psignal function, only it uses the signal number
-information from the si argument. The message strings can...
+...the signal number is not recognized sigaction(2) , the string Unknown signal is produced.
+The psiginfo function produces the same output as the psignal function, only it uses the signal number information from the si argument.
+The message strings can...
 
 intro(2)        introduction to system calls and error numbers
-...undefined signal to a signal(3) or kill(2) function). 23 ENFILE Too
-many open files in system . Maximum number...shell. Pathname A path
-name is a NUL -terminated character string starting with an optional
-slash \&/ , followed by zero or...
+...undefined signal to a signal(3) or kill(2) function).
+23 ENFILE Too many open files in system .
+Maximum number...shell.
+Pathname A path name is a NUL -terminated character string starting with an optional slash \&/ , followed by zero or...
 
-groff_mdoc(7)   reference for groff's mdoc implementation
-...Qq .Qq string ) , string ) , .Qq string Ns ), string ), .Sq .Sq
-string string .Em or...UNTITLED is used. The section number may be a
-number in the range 1...2, 3 and 9 error \&.\e"     and signal
-handling only. \&.\e" .Sh ERRORS \&.\e...
+dump_lfs(8)     filesystem backup
+...low estimates of the number of blocks to write, the number of tapes it...a string containing embedded formatting commands for strftime(3).
+The total formatted string is...in.
+If dump_lfs rdump_lfs receives a SIGINFO signal (see the status argument of stty...
 \end{lstlisting}
 
+In \textbf{Figure 1} the spell corrector can be seen in action along with the web
+interface that was developed using \textit{apropos-utils}.
 \begin{figure}[htp]
@@
 \end{figure}
+
 \section{Related Work}
@@
 \textit{man-db} [11] is a complete implementation of the man page documentation
-system and it is used on a number of GNU/Linux distributions.\textit{man-db}
+system and it is used on a number of GNU/Linux distributions. \textit{man-db}
 takes an interesting approach for indexing the man page data. Unlike the
-classical \textit{apropos}, it uses a Berkley DB database but still it's index
-is limited to the NAME section only. It adds an option `K' to man(1) to allow a
-crude full text search but it is not very efficient nor effective.
+classical \textit{apropos}, it uses a Berkley DB database but still its index
+is limited to the NAME section only. It adds an option `K' to \textit{man(1)} to
+allow a crude full text search but it is not very efficient nor effective.
 \end{description}
@@
 takes a novel approach. It indexes the keywords extracted from the man pages in a
-key-value store using btree(3) [13]. It also comes with it's own implementation
+key-value store using btree(3) [13]. It also comes with its own implementation
 of \textit{apropos} which performs search using this key-value store. The
@@
 \item[Work on Ranking Algorithm] \hfill \\
-A ranking algorithm based on probabilistic model [14] of information
-retrieval has been implemented to filter out the most relevant results and show
-them at the top. It is essentially based on the Okapi BM25F algorithm [15] and
+A ranking algorithm based on probabilistic model of information retrieval [14]
+has been implemented to perform relevance ranking of the search
+results. It is essentially based on the Okapi BM25F algorithm [15] and
 uses certain parameters whose values are usually dependent on the corpus and the
-search application. For example certain weight parameters are assigned to
-different sections of man pages. At the moment these values have been determined
+search application. For example, certain weight parameters have been assigned to
+different sections of man pages, signifying how important the information in a
+particular section is as compared to the rest of the sections. At the moment
+these values have been determined
 manually but one goal is to use some supervised machine learning techniques in
-the order to automate this.
+order to automate this.
 \end{description}
@@
 supplied with NetBSD and also on most of the man pages found in Pkgsrc. But there
-are perhaps a few corner cases still to be fixed. Besides that, another issue
-that
-is to be addressed is the parsing of the escape sequences which are used
-extensively in the \textit{man(7)} [16] based man pages. These issues are to be
-addressed in the coming days.
+are perhaps a few corner cases yet to be identified and fixed. Besides that,
+another issue that is to be addressed is the parsing of the escape sequences
+which are used extensively in the \textit{man(7)} [16] based man pages. These
+issues are to be addressed in the coming days.
 \end{description}
+\section{Availability}
+The code for this project is hosted on \textit{Github} and it is under active development. It can be obtained from:\newline
+ \emph{https://github.com/abhinav-upadhyay/apropos\_replacement}
 \section{Acknowledgement}

### 2012-02-28 apropos_replacement.tex
Make style consistent with Usenix. Add more details for submission to AsiaBSDCon.

@@
-\documentclass[titlepage, a4paper, 12pt]{article}
+\documentclass[letterpaper,twocolumn,10pt]{article}
+\usepackage{usenix,epsfig,endnotes}
 \usepackage{listings}
 \usepackage{color}
-\usepackage[pdftex]{graphicx}
-\usepackage{graphicx}
+\usepackage{times}
+\usepackage{algpseudocode}
+%\usepackage[pdftex]{graphicx}
 \lstset{ %
@@
 }
-\title{Apropos Replacement: Development of a full text search tool for man pages \newline
-(Initial Outline)}
-\author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
-Joerg Sonnenberger $<$joerg@NetBSD.org$>$}
+
 \begin{document}
+
+%don't want date printed
+\date{}
+
+%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
+\title{\Large \bf Apropos Replacement : Development of a full text search tool for man pages}
+
+%for single author (just remove % characters)
+\author{
+{\rm Abhinav Upadhyay}\\
+$<$er.abhinav.upadhyay@gmail.com$>$
+\and
+{\rm Joerg Sonnenberger}\\
+$<$joerg@NetBSD.org$>$
+} % end author
+
 \maketitle
-\section{Abstract}
-Unix like operating systems have withstood the test of time for 40 odd years for
-several technical and philosophical reasons. One of those reasons is the
-quality documentation they ship in the form of man pages, which are a single
-source of consultation for most of our routine work. However, so far, there has been a lack of
-good search tool to accompany this documentation, which would increase their
-usefulness manifolds.
 
-Traditionally, \textit{apropos} [1] has been there to act as a search
-interface but to a large extent it hasn't really lived up to its expectation.
-\textit{apropos} was
-developed in the early days of Unix when computing resources were scarce and
-that is the primary reason for its minimalistic and simple design. The biggest
-limitation of \textit{apropos} is its limited search capabilities.
+% Use the following at camera-ready time to suppress page numbers.
+% Comment it out when you first submit the paper for review.
+\thispagestyle{empty}
 
-This paper discusses a new implementation of \textit{apropos} which was done
-as part of \emph{Google Summer of Code 2011} [17]. The goal of this project was
-to replace the conventional apropos in NetBSD with a modern version which
-supports full text searches.
+\subsection*{Abstract}
+Manual pages are a key component of Unix like operating systems, they have
+played a significant role in the success of Unix over the years. Man pages are
+the most authentic source of reference for of a system administrator or a
+programmer. However, so far, there has been a lack of good search tool to make
+man pages more accessible. \\
+
+Traditionally, \textit{apropos(1)} has been there as a search interface but it
+was developed in the early days of Unix when computing resources were scarce
+and that is the primary reason for its simple design and limited search
+capabilities. \\
+
+This paper discusses a new implementation of \textit{apropos} done by
+Abhinav Upadhyay as part of
+Google Summer of Code 2011. The goal of this project was to replace the
+conventional apropos in NetBSD with a modern version which supports full text
+searches. \\
+
 \section{Introduction}
@@
 consisting of keywords hardly takes few hundreds of kilo bytes of disk space
-and performing search on a plain text file is quite easy.
+and performing search on a plain text file is quite easy. \\
 
@@
 usability, as the searches are limited to the keywords defined in the NAME
-section of the man pages. Only if a user knows the exact keywords do they get
+section of the man pages. Only if the users know the exact keywords do they get
 the appropriate results; otherwise most of
@@
 advancement in technology in order to solve the problem. This problem is made
-even simpler considering that the man pages consist of structured data.
+even simpler considering that the man pages consist of structured data. \\
 
@@
 can be easily afforded. These are necessary prerequisites for building an
-effective search tool.
+effective search tool. \\
 
@@
 are discussed along with brief details of how these were overcome as part of
-this project. Additionally, we compare and contrast our approach with other
-modern implementations available out there.
+this project. Additionally, a comparison of other modern implementations of apropos has been done. \\
 
@@
 the classical version of \textit{apropos} are shown and their shortcomings are
-analyzed.
+analyzed. \\
 
@@
 cannot search for keywords which are not usually specified in the title of a man
-page, for example a query like ``EINVAL'' would return no results.
+page, for example a query like ``EINVAL'' would return no results. \\
+
+{\tt \small
 \lstset{language = sh, caption={No results for free form queries}}
@@
 termcap database: nothing appropriate
-
-$ apropos ``signal number to string''
-signal number to string: nothing appropriate
 \end{lstlisting}
+}
 
@@
 is used in place of \textit{``directories''}, even though the two words are based
-on same root word.
-\lstset{language = sh, caption={No support for stems or words with same roots},}
+on same root word. \\
+
+{\tt \small
+\lstset{language = sh, caption={No support for stems or words with same root},}
 \begin{lstlisting}
@@
 
-$ apropos ``upgrading software package''
+$ apropos ``upgrading package''
 pkg_add (1) - a utility for installing and upgrading software package
 distributions
-$ apropos ``upgrading software packages''
-upgrading software packages: nothing appropriate
+
+$ apropos ``upgrading packages''
+upgrading packages: nothing appropriate
 \end{lstlisting}
+}
 
 Similarly, it is very common for users to misspell keywords in a query and \textit{apropos} has no support for it either.
+
+{\tt \small
 \lstset{language = sh, caption={No spelling correction},}
@@
 $ apropos ``copy strings''
-stpcpy, stpncpy, strcpy, strncpy (3) - copy strings
+stpcpy, stpncpy, strcpy, strncpy (3) - copy
+strings
 $ apropos ``coppy strings''
@@
 \end{lstlisting}
+}
 
@@
 Because of the way \textit{apropos} works, sometimes its output can be
-unintelligible and it can be very hard for the user to identify relevant results.
+unintelligible and it can be very hard for the user to identify relevant results. \\
 
+{\tt \small
 \lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},}
@@
 \end{lstlisting}
+}
+
 \subsection{Other Problems}
@@
 the way man pages are handled in NetBSD. The different aliases of the man pages
-are stored on the file system in the from of hard (or soft) links and these
-have to be mentioned in the makefiles explicitly using the MLINKS mechanism. This
+are stored on the file system in the from of hard (or symbolic) links and these
+have to be specified in the makefiles explicitly using the MLINKS mechanism. This
 approach works fine but it is a mess from maintenance point of view.
@@
 
-\section{Proposed Solution}
-A very simple and straightforward solution is proposed to solve these problems as
-part of this project.
-The idea is to parse and index
-the complete content (or at least most of the content) in the form of an
-inverted index [4] and use it to build a full text search
-interface. Having an index based on the complete content of the man pages solves
-many of the search
-related problems associated with the conventional \textit{apropos(1)} as noted
-before and discussed as follows:
+\section{Solution: A new apropos}
+This project proposes a very simple and straightforward solution to solve these
+problems and make man pages more usable. The idea is to exploit the inherent
+semantics and structure of the man pages. The \textit{mdoc(7)}
+macros are semantically quite rich, those macros combined with the context of the surrounding section or context in which they have been used, can be used
+as an indicator of the relevancy of the content. For example, the
+{\tt \small
+.Nm
+}
+macro when used inside of the
+{\tt \small
+NAME
+}
+section holds more significance than if used inside of any other section. Similarly the description of various \textit{errno} values in the
+\textit{intro(2)} man page has more important information than the mention of
+those \textit{errno} values in the
+{\tt \small
+RETURN VALUES
+}
+section of various man pages from section 3. In essence, it should be possible
+to parse and extract the structurally meaningful data
+out of man pages and index them in the form of an inverted index [4]. An
+inverted index is a specialized data structure for building search engines.
+The index combined with a ranking algorithm which exploits the structured nature of the data to give back more relevant results to the user, can be used to build a
+high quality search interface for manual pages.
+Such a search tool will solve many of the problems associated with the conventional \textit{apropos(1)} as noted
+before and discussed as follows: \\
+
 \begin{description}
@@
 are no longer limited to the the NAME section.
-For example, queries like \textit{``installing new software package''} will
+For example, queries like \textit{``installing new software package''} may
 now produce relevant results.
@@
 \textit{``Installing new packages''} and \textit{``install new package''} will
-return same results.
+return same results. \\
 
@@
 an md5 hash, the device id, inode number and modification time
-of the man page files are indexed and stored so
-as to support fast and hassle free update of the index as new man pages are
-installed or the old ones are modified/updated.
+of the man page files are indexed and stored.
+This allows for very fast and hassle free update of the index as new man pages are installed or the old ones are updated. \\
 
@@
 \end{description}
+
 \subsection{Tools Used}
@@
 man pages and building of an index of the
-data obtained from the parsing process. \textit{libmandoc} [6]
-and \textit{sqlite} [7] have been used for performing these the two tasks.
+data obtained from the parsing process. These are highly specific problems, and
+solving them from scratch would be a separate project in its own right, therefore this project tried to avoid reinventing the wheel and used existing
+tools and libraries which are battle tested and very successful.
+\textit{libmandoc} [6] from \textit{mdocml} [18] project has been used for parsing the man pages and \textit{sqlite} [7] for indexing and storing the parsed
+data on the file system.
+
 \begin{description}
 \item[\textit{libmandoc}] \hfill \\
-\textit{libmandoc} is a library interface to a validating compiler. It provides
+\textit{libmandoc} is a library interface to a validating compiler for man pages. It provides
 interface to parse and build an AST (Abstract Syntax Tree) of the man page. It
@@
 \end{description}
+
 \begin{description}
@@
 \end{description}
+
 \section{Implementation Details}
@@
 in this section.
+
+\subsection{makemandb}
+\textit{makemandb(8)} [9] is the key component of this implementation. It is a
+command line tool which traverses the filesystem, reads the raw man page source files, extracts the interesting data from them using the \textit{libmandoc} parser and then stores that data in an FTS table using \textit{sqlite}.
+\\
+
 \begin{description}
-\item[makemandb] \hfill \\
-\textit{makemandb} [9] is the key component of this implementation. It is a
-command line tool which
-traverses the filesystem, reads the raw man page source files, feeds them to the
-\textit{libmandoc} parser and then stores the extracted data in the database
-using \textit{sqlite}.
+\item[Operation of makemandb] \hfill \\
+\textit{makemandb} uses a two pass algorithm to index the man pages. In the first pass it obtains the list of directories containing man page files from
+\textit{man.conf} and starts traversing those directories. It obtains the
+\textit{\{dev\_t, ino\_t, mtime\}} of all the files using \textit{stat(2)}.
+A similar set of metadata is stored in the database (referring to the last successful indexing operation), \textit{makemandb} takes a difference (the set difference operation) of the two sets of metadata to obtain the list of man page files on the file system which are either newly installed (new \textit{\{dev\_t, ino\_t\}} pairs) or they have been updated (changed \textit{mtime}).
+\\
+
+In the second pass \textit{makemandb} generates md5 checksum of the files obtained from the previous stage and for each of these checksums, it checks in
+the db, whether this md5 checksum already exists in the db or not.
+If the md5 checksum is already present in the database, then this was just a false alarm and \textit{makemandb} does not need to parse the file, it simply updates the metadata of that file in the database.
+In case the md5 checksum of a file does not already exist in the database, then that means the file is either a newly installed man page or an older copy of a man page was updated,
+\textit{makemandb} feeds such man pages to the parser and extracts interesting
+data out of them, later on storing the data in the FTS table in the database.
 \end{description}
+
 \begin{description}
-\item[apropos] \hfill \\
-This is the version of \textit{apropos} written from scratch utilizing the
-full text search functionality of \textit{sqlite}. Unlike the classical version
-of \textit{apropos}, it only displays the top 10 results relevant to the user
-query and most of the times this is sufficient as will be seen later. Also, it
-shows a brief snippet of matching text for each of the search results, making it
-more easy to identify the relevant documents.
+\item[Database Schema] \hfill \\
+During the initial stage of the project, the structure of the database was kept
+simple. The FTS table consisted of 3 columns:
+{\tt
+name, name\_desc, desc
+}
+The
+{\tt
+name
+}
+and
+{\tt
+name\_desc
+}
+columns stored the name of the man page and the one line description from the
+{\tt
+NAME
+}
+section, while the
+{\tt
+desc
+}
+column stored the content from the rest of the sections. This approach worked
+quite well for a small set of man pages (for example the 4000 or so man pages in
+the base set of NetBSD).
+However, as the number of documents were increased (for example including man pages from pkgsrc), the quality of search started deteriorating.
+This was mainly because bulk of the parsed data was being stored
+in the same column in the database and the ranking algorithm had no way of
+identifying more relevant results apart from the number of matches in any page. \\
+
+To rectify this, first there was an attempt to try out better ranking schemes
+(the various ranking schemes that were tried out during the development of the
+project are discussed later). Better ranking schemes required storing precomputed
+term weights [19] on the file system, this almost doubled the storage requirements, therefore such ranking schemes were discarded later on, and the
+database schema was decomposed further into more columns. The decomposition into
+more columns was done to represent the most commonly occurring sections in usual Unix man pages, for example
+{\tt NAME, DESCRIPTION, LIBRARY, RETURN VALUES, EXIT STATUS, ERRORS}
+etc. Such a decomposition allowed for an elaborate ranking algorithm, which could
+assign different weights to each of these columns, based on their relevancy. The
+final schema of the database is shown in {\bf Listing 5}
 \end{description}
-\begin{description}
-\item[apropos-utils] \hfill \\
+
+\subsection{apropos}
+\textit{apropos} was written from scratch to use the FTS index created by
+\textit{makemandb}. Since, unlike the traditional \textit{apropos}, this version
+of \textit{apropos} is not limited to searching within only the {\tt NAME}
+section, the resulting
+number of search results is usually quite high, therefore new \textit{apropos}
+employs a
+sophisticated ranking algorithm to filter out the most relevant results and rank
+them up. To avoid cluttering the output and make the user interface clean, the
+new \textit{apropos} displays only the top 10 results by default with options
+to display more results if required. During the development and testing of the
+project it has been observed that, for a reasonable query, the top 10 results
+are most often sufficient. \\
+
+Another key aspect of any search application is to filter out or avoid stop-words
+. Words like \textit{``the'', ``a'', ``an'', ``'this''} etc. come under the
+category of stop-words, words which are \emph{very} commonly used in the
+language. Stop-words usually skew the search results because of their sheer
+frequency in the corpus. The usual practice in the information retrieval world
+is to filter such stop-words while building the index, however, in case of this
+project, it proved to be non-trivial within the given time constraints.
+Therefore it was decided that, rather than eliminating stop-words from the index,
+a reasonable trade off can be made by filtering out any stop-words from the
+user's search query and querying the database for only the keywords which do
+not come under the category of stop-words. \\
+
+{\tt \small
+\lstset{language = XML, caption={Database Schema},}
+\begin{lstlisting}
+The Database has three tables at present:
+
+(1) mandb:
+    The main FTS table which contains all
+    the content parsed from man pages
+
+  COLUMN NAME       DESCRIPTION
+  1. section        Section number
+  2. name           The name of the page  
+  3. name_desc      Short description from
+                    NAME section  
+  4. desc           Contains the content
+                    from DESCRIPTION
+                    section and any other
+                    section which is not
+                    stored in a separate
+                    column.
+  5. lib            The LIBRARY section
+  6. return_vals    RETURN VALUES section
+  7. env            ENVIRONMENT section
+  8. files          FILES section
+  9. exit_status    EXIT STATUS section
+  10. diagnostics   DIAGNOSTICS section
+  11. errors        ERRORS section
+  12. md5_hash      An md5 hash of the
+                    contents of the man
+                    page (UNIQUE).
+(2) mandb_meta:
+    This table maintains essential
+    metadata of all the indexed
+    man page files.
+
+  COLUMN NAME       DESCRIPTION
+  1. device         (dev_t)Logical device
+                    number from stat(2)
+  2. inode          (ino_t)Inode number
+                    from stat(2)
+  3. mtime          Last modification time
+                    from stat(2)
+  4. file           Absolute path name
+                    (UNIQUE constraint)
+  5. md5_hash       MD5 Hash of the man
+                    page
+  6. id             A unique integer ID
+                    referring to a page
+                    in mandb (PRIMARY KEY)
+
+(3) mandb_links:
+    This is an index of all the hard/soft
+    links of the man pages. The list of
+    the linked pages is usually obtained 
+    from the multiple .Nm entries in the
+    page.
+
+  COLUMN NAME       DESCRIPTION
+  1. link           The name of the hard/
+                    soft link (UNIQUE index) 
+  2. target         Name of the target
+                    page to which it
+                    points  
+  3. section        The section number  
+  4. machine        The machine
+                    architecture (if any)
+                    for which the page is
+                    relevant.
+\end{lstlisting}
+}
+
+\subsection{apropos-utils}
 \textit{apropos-utils} [10] is a small library interface provided with this
@@
 is to develop different interfaces on top of it for different
-use cases. For example a small CGI application was built using it for doing
+use cases. For instance a CGI front end has been built using it for doing
 the searches from a web browser, similarly an IRC bot was also developed utilizing this interface.
+
+\subsection{Ranking Algorithm}
+The ranking algorithm is the most interesting and most crucial component of
+any search application, it is the deciding factor of the usefulness of the
+application. This project took several stabs at coming up with a suitable ranking
+algorithm for \textit{apropos}.
+
+\begin{description}
+\item[1.] \hfill \\
+Initially the database schema was quite simple, it consisted of only three
+columns
+{\tt 
+name, name\_desc, desc
+}
+(as described previously). At this point, there weren't too many documents in
+the corpus, therefore nothing sophisticated was required. The basic intuition was
+that, a match found in the
+{\tt NAME} section of a man page has more weight as compared to a match found
+in any other section. This ranking scheme worked well for a small set of man
+pages in the corpus.
+\end{description}
+
+\begin{description}
+\item[2.] \hfill \\
+As more and more man pages were being added to the corpus for testing purposes,
+the quality of search results started to dilute. At this point of time, a
+completely new approach was adopted for ranking the results. In the literature
+related to information retrieval, \textit{tf-idf} [19] weights based ranking models are very common.
+The \textit{tf} in \textit{tf-idf} stands for \emph{Term Frequency} and \textit{idf} stands for \emph{Inverse Document Frequency}.
+\\
+
+{\bf Term Frequency}: Term frequency refers to the count of the number of times
+a given term
+{\tt \small
+t
+}
+appears in a given document
+{\tt \small
+d
+} \\
+
+{\bf Inverse Document Frequency:} The \textit{idf} of a term
+{\tt \small
+t
+}
+is the number of documents in which the term appears \textit{at least once}. \\
+
+Term frequency is a \textit{local} factor, it is concerned only with the number
+of occurrences of the search terms in one particular document at a time.
+While inverse document frequency is a \textit{global} factor, in the sense that,
+it indicates the discriminating power of a term. If a term appears in only a
+selected set of documents, then that term separates those set of
+documents from the rest. Therefore, ranking obtained by combining these two factors
+brings up more relevant documents.
+
+The weight of a term
+{\tt \small t} in document {\tt \small d} is calculated by the following
+formula:
+
+\begin{center}
+\framebox{\parbox[b]{2 in}{$weight  = tf \times idf$}}
+\end{center}
+Where \textit{tf} = Term frequency of term {\tt \small t} in document
+{\tt \small d} \\
+
+Inverse document frequency is calculated using the following formula:
+\begin{center}
+\framebox{\parbox[b]{2 in}{$idf = log (\frac{N}{N_t})$}}
+\end{center}
+Where $N$ = Total number of documents in the corpus \\
+$N_t$ = Number of documents in which term $t$ occurs (at least once). \\
+
+So for a term which appears in only one document it will have
+$idf = log(n)$,
+while a term which appears in all the documents, it will have
+$idf = log(1) = 0$
+
+For example a term like \textit{``the''} will have a high
+\textit{term frequency} in any
+document, but at the same time it will have a lower \textit{inverse document frequency} (almost close to $0$), which will nullify its effect on the quality of search results.
+
+A lot of research has been done on \textit{tf-idf} weights based ranking
+algorithms and various techniques have been proposed over the years. According
+to a survey done by \textit{Salton} and \textit{Buckley} in 1988 [21], the
+following ranking scheme was found to be most effective:
+
+\begin{center}
+\framebox{\parbox[b]{2 in}{$\frac{tf \cdot log(\frac{N}{N_t})}{\sqrt{\sum{(tf \cdot log(\frac{N}{N_t}))^2}}}$}}
+\end{center}
+
+The implementation of the above scheme proved to be \emph{very} slow. It required
+too many computations and all of these were required to be done for each
+search result separately to compute its relevance weight. In an state of the
+art search application, the index would usually store precomputed \textit{tf-idf}
+weights on the file system, in which case the overhead of computing weights of
+each individual search result would require very less work, leading to better
+performance. An attempt was made to compute the \textit{tf-idf} weights while
+indexing the man pages and store them in a separate table. This lead to high
+quality search results but it also brought up a serious issue. Storing
+precomputed weights on the file system, more than doubled the storage
+requirements of the database index. As a concrete example, it took close
+to $90 MB$ to index about $8000$ documents. Without the precomputed weights, 
+the database size requirement was close to $45 MB$ for the same number of pages.
+\end{description}
+
+\begin{description}
+\item[3.] \hfill \\
+Since the conventional \textit{apropos} required only a few hundred kilobytes of
+disk space, the disk space requirements of new \textit{apropos} seemed
+hyperbolic, therefore it was decided later on to look for alternative ranking
+schemes. At this point the database schema was decomposed into several columns
+representing some of the most common sections found in man pages
+(see {\bf Listing 5}).
+
+At this point a fast yet sophisticated ranking algorithm was adopted.
+\emph{OKAPI BM25F} [15] is considered one of the most successful probabilistic
+models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
+scheme but it takes into account for the structure of the data. It allows for
+separate weights to be assigned for different parts of a structured document to
+come up with better relevance rankings. This scheme works very well for man pages
+because of their highly structured content. The algorithm is described in pseudo-code below. \textit{apropos} calls this function for each of the document
+obtained as part of the result set for the query and computes its relevancy
+weight. The documents are ranked in decreasing order or the weights returned
+from this function. \\
+
+In the following algorithm: \\
+{\tt
+\lstset{language = sh, caption={},}
+\begin{lstlisting}
+nhitcount =  Number of occurrences of
+             phrase p in column c in
+             current document
+
+nglobalhitcount = Number of occurrences of
+                  phrase p in column c in
+                  all the documents.
+
+ndocshitcount = Number of documents in
+                which phrase p occurs
+                in column c, at least
+                once.
+\end{lstlisting}
+}
+
+\begin{algorithmic}
+\State ${\tt tf} \gets 0.0$
+\State ${\tt idf} \gets 0.0$
+\State ${\tt k} \gets 3.5$
+\Comment 
+{k is an experimentally determined parameter}
+\State ${\tt doclen} \gets $ length of the current document
+\State ${\tt ndoc} \gets $ Total number of documents in the corpus
+\For {each phrase {\tt p} in the user query}
+\For {each column {\tt c} in the FTS table}
+\State $w \gets $ weight for column {\tt c}
+\State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
+\State $tf \gets tf + \frac{(nhitcount \times w)}{(nglobalhitcount \times doclen)}$
+\EndFor
+\EndFor
+\State $score \gets $ $\frac{(tf \times idf)}{(k + tf)}$ \\
+\Return $score$
+\end{algorithmic}
+
 \end{description}
 \section{Results}
-This section shows results of some of the sample queries on the version of
-developed as part of this project
-\textit{apropos} to demonstrate how it solves many of the problems cited earlier
-with the classical version of \textit{apropos}.
-\footnote{Although this implementation of \textit{apropos} returns 10 results
-in normal cases for a query but in the following listings the output has been
+This section shows results of some of the sample queries on new \textit{apropos}
+to demonstrate how it performs as compared to the traditional version.
+\endnote{Although this implementation of \textit{apropos} by default returns 10
+results for a query but in the following listings the output has been
 snipped to save space
-}
-\lstset{language = sh, caption={Add new user},}
+} \\
+
+{\tt \small
+\lstset{language = XML, caption={Add new user},}
 \begin{lstlisting}
 $ apropos ``add new user''
-ssh-add(1)      adds private key identities to the authentication agent...on the command line.
-If any file requires a passphrase, ssh-add asks for the passphrase from the user.
-The passphrase is read from the user's tty.
-ssh-add retries the last passphrase if multiple identity files are given...
+ssh-add(1)      adds private key identities to
+the authentication agent...on the command line.
+If any file requires a passphrase, ssh-add asks
+for the passphrase from the user. The
+passphrase is read from the user's tty. ssh-add
+retries the last passphrase if multiple
+identity files are given...
 
-chpass(1)       add or change user database information
+chpass(1)       add or change user database
+information
 add or change user database information
@@
 useradd(8)      add a user to the system
-The useradd utility adds a user to the system, creating and populating a home directory if necessary.
-Any skeleton files will be provided for the new user if they exist in the skel-dir directory (see the k option).
-Default...
+The useradd utility adds a user to the system,
+creating and populating a home directory if
+necessary. Any skeleton files will be provided
+for the new user if they exist in the skel-dir
+directory (see the k option). Default...
 .
@@
 \end{lstlisting}
-\lstset{language = sh, caption={make directory},}
+}
+
+{\tt \small
+\lstset{language = XML, caption={make directory},}
 \begin{lstlisting}
@@
 make(1) maintain program dependencies
-...CURDIR A path to the directory where make was executed.
-Refer to the description of PWD for more details.
-MAKE The name that make was executed with argv[0] .
-For compatibility make also sets .MAKE with the same value.
-The...
+...CURDIR A path to the directory where make
+was executed. Refer to the description of PWD
+for more details. MAKE The name that make was
+executed with argv[0].
+For compatibility make also sets .MAKE with the
+same value. The...
 
@@
 ln(1)   make links
-...a directory in which to place the link; otherwise it is placed in the current directory.
-If only the directory is specified, the link will be made to the last component of source_file .
-Given more than two arguments, ln makes...
+...a directory in which to place the link;
+otherwise it is placed in the current directory
+If only the directory is specified, the link
+will be made to the last component of
+source_file . Given more than two arguments,
+ln makes...
 
 mkfifo(1)       make fifos
-make fifos...of a=rw mkfifo requires write permission in the parent directory. mkfifo exits 0 if successful, and >0 if an...
+make fifos...of a=rw mkfifo requires write
+permission in the parent directory. mkfifo
+exits 0 if successful, and >0 if an...
 
 mkdir(2)        make a directory file
-...will contain the directory has been exhausted.
-EDQUOT The user's quota of inodes on the file system on which the directory is being created has been exhausted.
-EIO An I/O error occurred while making the directory entry or...
+...will contain the directory has been
+exhausted. EDQUOT The user's quota of
+inodes on the file system on which the
+directory is being created has been
+exhausted. EIO An I/O error occurred
+while making the directory entry or...
 \end{lstlisting}
-\lstset{language = sh, caption={signal number to string},}
+}
+
+{\tt \small
+\lstset{language = XML, caption={signal number to string},}
 \begin{lstlisting}
@@
 psignal(3)      system signal messages
-...the signal number is not recognized sigaction(2) , the string Unknown signal is produced.
-The psiginfo function produces the same output as the psignal function, only it uses the signal number information from the si argument.
-The message strings can...
+...the signal number is not recognized
+sigaction(2) , the string Unknown signal
+is produced. The psiginfo function produces
+the same output as the psignal function,
+only it uses the signal number information
+from the si argument. The message strings can...
 
-intro(2)        introduction to system calls and error numbers
-...undefined signal to a signal(3) or kill(2) function).
-23 ENFILE Too many open files in system .
-Maximum number...shell.
-Pathname A path name is a NUL -terminated character string starting with an optional slash \&/ , followed by zero or...
+intro(2)        introduction to system calls
+and error numbers
+...undefined signal to a signal(3) or kill(2)
+function). 23 ENFILE Too many open files in
+system . Maximum number...shell. Pathname A
+path name is a NUL -terminated character
+string starting with an optional slash,
+followed by zero or...
 
 dump_lfs(8)     filesystem backup
-...low estimates of the number of blocks to write, the number of tapes it...a string containing embedded formatting commands for strftime(3).
-The total formatted string is...in.
-If dump_lfs rdump_lfs receives a SIGINFO signal (see the status argument of stty...
+...low estimates of the number of blocks to
+write, the number of tapes it...a string
+containing embedded formatting commands for
+strftime(3). The total formatted string
+is...in. If dump_lfs rdump_lfs receives a
+SIGINFO signal (see the status argument of
+stty...
 \end{lstlisting}
+}
+
+\begin{figure*}[htp]
+\begin{center}
+\includegraphics [scale=0.36]{/home/abhinav/development/AsiaBSDCon/spell.png}
+\caption{The spell corrector and the CGI frontend in action}
+\label{}
+\end{center}
+\end{figure*}
 
 In \textbf{Figure 1} the spell corrector can be seen in action along with the web
-interface that was developed using \textit{apropos-utils}.
-\begin{figure}[htp]
-\includegraphics[scale=0.30]{/home/abhinav/development/AsiaBSDCon/spell.png}
-\caption{The spell corrector and the web interface in action}
-\label{}
-\end{figure}
+interface that was developed using \textit{apropos-utils}. \\
 
@@
 main key point of this implementation is that it exploits the semantic structure
-of the man pages.
+but rather than indexing the complete content, it plucks out specific pieces of
+information from the man pages, for example Author names, function names,
+header file names, etc.
+from the man pages. It is more sophisticated and much more useful than classic
+\textit{apropos}, but it is still essentially a keyword lookup based
+implementation.
 \end{description}
+
 \section{Future Work}
@@
 \item[Work on Ranking Algorithm] \hfill \\
-A ranking algorithm based on probabilistic model of information retrieval [14]
-has been implemented to perform relevance ranking of the search
-results. It is essentially based on the Okapi BM25F algorithm [15] and
+The ranking algorithm is based on the probabilistic model of information
+retrieval [14]results. It
 uses certain parameters whose values are usually dependent on the corpus and the
@@
 manually but one goal is to use some supervised machine learning techniques in
-order to automate this.
+order to automate this so that more better search results can be obtained.
 \end{description}
+
 \begin{description}
-\item[Fix Some Loose Ends In Parsing of man pages] \hfill \\
-Although the parsing routine is working fine for most purposes on the man pages
-supplied with NetBSD and also on most of the man pages found in Pkgsrc. But there
-are perhaps a few corner cases yet to be identified and fixed. Besides that,
-another issue that is to be addressed is the parsing of the escape sequences
-which are used extensively in the \textit{man(7)} [16] based man pages. These
-issues are to be addressed in the coming days.
+\item[Using external storage] \hfill \\
+A new feature is under development in \textit{Sqlite}, to support external
+storage option in FTS databases. This option would allow building the FTS
+index without actually storing any content in the database itself (except for
+the data required to maintain the indexes). This will save bulk of the disk
+space currently required by \textit{apropos} database. The disk space thus
+saved might also allow for experiments with ranking algorithms which require
+storing additional metadata on the disk.
 \end{description}
+
 \section{Availability}
-The code for this project is hosted on \textit{Github} and it is under active development. It can be obtained from:\newline
- \emph{https://github.com/abhinav-upadhyay/apropos\_replacement}
+The code for this project has been imported into the NetBSD source tree and
+being maintained there. Experimental work is still being done in the \textit
+{github} repository of the project. It can be obtained from:\newline
+
+{\tt
+ \emph{https://github.com/abhinav-upadhyay/
+ apropos\_replacement}
+}
+
 \section{Acknowledgement}
@@
 man pages for this project. Thanks to \textbf{Petra Zeidler} for administering
-the GSoC program for \textit{The NetBSD Foundation}.
+the GSoC program for \textit{The NetBSD Foundation}. \\
+
 \begin{thebibliography}{20}
 \bibitem{1}
-\emph{NetBSD manual page for apropos(1)}
-\newline http://netbsd.gw.com/cgi-bin/man-cgi?apropos++NetBSD-5.1
+\emph{NetBSD manual page for the old version of apropos}
+\newline
+{\tt
+http://netbsd.gw.com/cgi-bin/
+man-cgi?apropos++NetBSD-5.1
+}
 
 \bibitem{2}
-\emph{NetBSD manual page for makewhatis(1)}
-\newline http://netbsd.gw.com/cgi-bin/man-cgi?makewhatis++NetBSD-5.1
+\emph{NetBSD manual page for makewhatis(8)}
+\newline
+{\tt
+http://netbsd.gw.com/cgi-bin/
+man-cgi?makewhatis++NetBSD-5.1
+}
 
@@
 libmandoc}
-\newline http://mdocml.bsd.lv/mandoc.3.html
+\newline
+{\tt
+http://mdocml.bsd.lv/mandoc.3.html
+}
 
@@
 \emph{Sqlite home page}
-\newline http://sqlite.org
+\newline
+{\tt
+http://sqlite.org
+}
 
@@
 \emph{Sqlite FTS3 and FTS4 Extensions}
-\newline  http://sqlite.org/fts3.html
+\newline
+{\tt
+http://sqlite.org/fts3.html
+}
 
 \bibitem{9}
-\emph{Online manual page for makemandb(1)}
-\newline http://netbsd-soc.sourceforge.net/projects/apropos\_replacement/makemandb.html1
+\emph{Online manual page for makemandb(8)}
+\newline
+{\tt
+http://netbsd.gw.com/cgi-bin/
+man-cgi?makemandb++NetBSD-current
+}
 
@@
 \emph{Online manual page for apropos-utils(3)}
-\newline http://netbsd-soc.sourceforge.net/projects/apropos\_replacement/apropos-utils.html3
+\newline
+{\tt
+http://netbsd-soc.sf.net/projects/
+apropos\_replacement/apropos-utils.html3
+}
 
@@
 \emph{man-db, the on-line manual database}
-\newline http://man-db.nongnu.org/
+\newline
+{\tt
+http://man-db.nongnu.org/
+}
 
 \bibitem{12}
-\emph{Online manual page for mandocdb(1)}
-\newline http://mdocml.bsd.lv/mandocdb.8.html
+\emph{Online manual page for mandocdb(8)}
+\newline
+{\tt
+http://mdocml.bsd.lv/mandocdb.8.html
+}
 
@@
 \emph{NetBSD online manual page for btree(3)}
-\newline http://netbsd.gw.com/cgi-bin/man-cgi?btree+3+NetBSD-5.1
+\newline
+{\tt
+http://netbsd.gw.com/cgi-bin/
+man-cgi?btree+3+NetBSD-5.1
+}
 
@@
 \emph{Online manual page for man(7)}
-\newline http://mdocml.bsd.lv/man.7.html
+\newline
+{\tt
+http://mdocml.bsd.lv/man.7.html
+}
 
@@
 \emph{Google Summer of Code home page}
-\newline http://code.google.com/soc/
+\newline
+{\tt
+http://code.google.com/soc/
+}
 
@@
 \emph {The mdocml project home page}
-\newline http://mdocml.bsd.lv
+\newline
+{\tt
+http://mdocml.bsd.lv
+}
+
+\bibitem{19}
+Jones, Sparck K.
+\emph {A statistical interpretation of term specificity and its application in retrieval.}
+Journal of Documentation
+Volume 28 Number 1 1972 pp. 11-21
+\newline
+{\tt
+http://mdocml.bsd.lv
+}
+
 \end{thebibliography}
+
+\theendnotes
+
 \end{document}

### 2012-02-28 apropos_replacement.tex
Fix some grammar

@@
 \usepackage{times}
-\usepackage{algpseudocode}
+\usepackage{algorithm}% http://ctan.org/pkg/algorithm
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
 %\usepackage[pdftex]{graphicx}
@@
 algorithms and various techniques have been proposed over the years. According
-to a survey done by \textit{Salton} and \textit{Buckley} in 1988 [21], the
+to a survey done by \textit{Salton} and \textit{Buckley} in 1988 [20], the
 following ranking scheme was found to be most effective:
@@
 At this point a fast yet sophisticated ranking algorithm was adopted.
-\emph{OKAPI BM25F} [15] is considered one of the most successful probabilistic
+\emph{Okapi BM25F} [15] is considered one of the most successful probabilistic
 models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
@@
 obtained as part of the result set for the query and computes its relevancy
-weight. The documents are ranked in decreasing order or the weights returned
+weight. The documents are ranked in decreasing order of the weights returned
 from this function. \\
 
-In the following algorithm: \\
 {\tt
-\lstset{language = sh, caption={},}
+\lstset{language = sh, caption={Definition of important entities used in
+algorithm \ref{alg1}},}
 \begin{lstlisting}
@@
 }
-
-\begin{algorithmic}
+\begin{algorithm}
+\caption{Compute Relevance Weight of a Document for a Given User Query}
+\label{alg1}
+\begin{algorithmic}[1]
+\Require{User query {\tt q}}
+\Require{Document {\tt d} whose weight needs to be computed}
 \State ${\tt tf} \gets 0.0$
@@
 \State ${\tt ndoc} \gets $ Total number of documents in the corpus
-\For {each phrase {\tt p} in the user query}
+\For{each phrase {\tt p} in {\tt q}}
 \For {each column {\tt c} in the FTS table}
@@
 \end{algorithmic}
+\end{algorithm}
+\end{description}
 
-\end{description}
 \section{Results}
@@
 to demonstrate how it performs as compared to the traditional version.
-\endnote{Although this implementation of \textit{apropos} by default returns 10
-results for a query but in the following listings the output has been
+\endnote{Although the new \textit{apropos} by default returns 10
+results for a query but in the listings the output has been
 snipped to save space
@@
 but rather than indexing the complete content, it plucks out specific pieces of
-information from the man pages, for example Author names, function names,
+information from the man pages, for example author names, function names,
 header file names, etc.
@@
 The ranking algorithm is based on the probabilistic model of information
-retrieval [14]results. It
+retrieval [14]. It
 uses certain parameters whose values are usually dependent on the corpus and the
@@
 manually but one goal is to use some supervised machine learning techniques in
-order to automate this so that more better search results can be obtained.
+order to automate this to improve the quality of search results further.
 \end{description}
@@
 30:107-117, 1998
+
 \bibitem{4}
@@
 2008
+
 \bibitem{5}
@@
 Volume 28 Number 1 1972 pp. 11-21
-\newline
-{\tt
-http://mdocml.bsd.lv
-}
+
+\bibitem{20}
+Salton, Gerard; Buckley C.
+\emph {Term-Weighting Approaches in Automatic Text Retrieval.}
+Information Processing \& Management Vol. 24, No. 5, pp. 513-523,
+1988
 

### 2012-02-29 apropos_replacement.tex
Fix abstract
Language improvement

@@
 played a significant role in the success of Unix over the years. Man pages are
-the most authentic source of reference for of a system administrator or a
-programmer. However, so far, there has been a lack of good search tool to make
+the most authentic source of reference for a system administrator or a
+programmer. However, there has been a lack of good search tool to make
 man pages more accessible. \\
@@
 This paper discusses a new implementation of \textit{apropos} done by
-Abhinav Upadhyay as part of
-Google Summer of Code 2011. The goal of this project was to replace the
+Abhinav Upadhyay and mentored by Joerg Sonnenberger as part of
+Google Summer of Code 2011, for The NetBSD Foundation. The goal of this project
+was to replace the
 conventional apropos in NetBSD with a modern version which supports full text
@@
 This simplified design of \textit{apropos} resulted in limited utility and
-usability, as the searches are limited to the keywords defined in the NAME
-section of the man pages. Only if the users know the exact keywords do they get
+usability. Only if the users know the exact keywords do they get
 the appropriate results; otherwise most of
@@
 In the modern
-computing world where hard problems like searching the World Wide Web have been
+computing world, where hard problems like searching the World Wide Web have been
 solved [3] to a sufficient degree, it makes perfect sense to leverage the
-advancement in technology in order to solve the problem. This problem is made
-even simpler considering that the man pages consist of structured data. \\
+advancement in technology in order to come up with a better search tool for
+man pages. \\
 
@@
 used in the NAME section of the man pages. This means that the users do not have
-a whole lot of choice for specifying keywords in their queries. Besides they
-cannot search for keywords which are not usually specified in the title of a man
-page, for example a query like ``EINVAL'' would return no results. \\
+a whole lot of options for specifying keywords in their queries. Besides this,
+they cannot search for keywords which are not usually specified in the title of
+a man page, for example a query like {\tt EINVAL} would return no results. \\
 
 {\tt \small
-\lstset{language = sh, caption={No results for free form queries}}
+\lstset{language = XML, caption={No results for free form queries}}
 \begin{lstlisting}
@@
 Another major limitation of the classical version of \textit{apropos} is that
-it is not smart enough to provide basic natural language processing constructs,
+it is not smart enough to provide support for basic natural language processing
+constructs,
 like stemming or spelling corrections.
@@
 {\tt \small
-\lstset{language = sh, caption={No support for stems or words with same root},}
+\lstset{language = XML, caption={No support for stems or words with same root},}
 \begin{lstlisting}
@@
 mkdir (1) - make directories
+
 $ apropos ``make directory''
@@
 $ apropos ``upgrading package''
-pkg_add (1) - a utility for installing and upgrading software package
-distributions
+pkg_add (1) - a utility for installing and
+upgrading software package distributions
 
@@
 strings
+
 $ apropos ``coppy strings''
@@
 problems and make man pages more usable. The idea is to exploit the inherent
-semantics and structure of the man pages. The \textit{mdoc(7)}
-macros are semantically quite rich, those macros combined with the context of the surrounding section or context in which they have been used, can be used
+semantics and structure of the man pages. The \textit{mdoc(7)} [21] and
+\textit{man(7)} [16] macros used for writing man pages are semantically quite
+rich, those macros combined with the context of the surrounding section of the
+man page in which they have been used, can act
 as an indicator of the relevancy of the content. For example, the
@@
 }
-section of various man pages from section 3. In essence, it should be possible
+section of various man pages from section 3. \\
+
+In essence, it should be possible
 to parse and extract the structurally meaningful data
-out of man pages and index them in the form of an inverted index [4]. An
-inverted index is a specialized data structure for building search engines.
-The index combined with a ranking algorithm which exploits the structured nature of the data to give back more relevant results to the user, can be used to build a
+out of man pages and index them in the form of an inverted index [4]. The index
+combined with a ranking algorithm which exploits the structured nature of the
+data to give back more relevant results to the user, can be used to build a
 high quality search interface for manual pages.
@@
 data obtained from the parsing process. These are highly specific problems, and
-solving them from scratch would be a separate project in its own right, therefore this project tried to avoid reinventing the wheel and used existing
+solving them from scratch would be a separate project in its own right,
+therefore this project tried to avoid reinventing the wheel and used existing
 tools and libraries which are battle tested and very successful.
-\textit{libmandoc} [6] from \textit{mdocml} [18] project has been used for parsing the man pages and \textit{sqlite} [7] for indexing and storing the parsed
+\textit{libmandoc} [6] from \textit{mdocml} [18] project has been used for
+parsing the man pages and \textit{sqlite} [7] for indexing and storing the parsed
 data on the file system.
@@
 \section{Implementation Details}
-Due to space constraints it is not possible to go into enough implementation
-details, the most important components of this project are described in brief
-in this section.
 
@@
 }
-section, while the
+section respectively, while the
 {\tt
@@
 in the same column in the database and the ranking algorithm had no way of
-identifying more relevant results apart from the number of matches in any page. \\
+identifying more relevant results except from identifying whether the match was found in the {\tt NAME} section or any other section. \\
 
@@
 {\tt NAME, DESCRIPTION, LIBRARY, RETURN VALUES, EXIT STATUS, ERRORS}
-etc. Such a decomposition allowed for an elaborate ranking algorithm, which could
+etc. Such a decomposition allowed for an elaborate ranking scheme, which could
 assign different weights to each of these columns, based on their relevancy. The
@@
 to display more results if required. During the development and testing of the
-project it has been observed that, for a reasonable query, the top 10 results
-are most often sufficient. \\
+project it has been observed that, for a query, most often than not the top 10
+results are sufficient. \\
 
@@
 . Words like \textit{``the'', ``a'', ``an'', ``'this''} etc. come under the
-category of stop-words, words which are \emph{very} commonly used in the
+category of stop-words, these are the words which are \emph{very} commonly used
+in the
 language. Stop-words usually skew the search results because of their sheer
@@
 The Database has three tables at present:
+1. mandb
+2. mandb_meta
+3. mandb_links
 
@@
 the quality of search results started to dilute. At this point of time, a
-completely new approach was adopted for ranking the results. In the literature
-related to information retrieval, \textit{tf-idf} [19] weights based ranking models are very common.
+completely new approach was adopted for ranking the results. In the information
+retrieval literature, \textit{tf-idf} [19] weights based ranking models are very common.
 The \textit{tf} in \textit{tf-idf} stands for \emph{Term Frequency} and \textit{idf} stands for \emph{Inverse Document Frequency}.
@@
 
-{\bf Term Frequency}: Term frequency refers to the count of the number of times
-a given term
-{\tt \small
-t
-}
-appears in a given document
-{\tt \small
-d
-} \\
+{\bf Term Frequency}: The term frequency of a term {\tt \small t} in a document
+{\tt d} refers to the count of the number of times the term {\tt \small t}
+appears in the document {\tt \small d } \\
 
@@
 of occurrences of the search terms in one particular document at a time.
-While inverse document frequency is a \textit{global} factor, in the sense that,
+While inverse document frequency is a \textit{global} factor, in the sense that
 it indicates the discriminating power of a term. If a term appears in only a
@@
 documents from the rest. Therefore, ranking obtained by combining these two factors
-brings up more relevant documents.
+brings up more relevant documents. \\
 
@@
 
-So for a term which appears in only one document it will have
+So for a term which appears in only one document, it will have
 $idf = log(n)$,
 while a term which appears in all the documents, it will have
-$idf = log(1) = 0$
-
+$idf = log(1) = 0$.
 For example a term like \textit{``the''} will have a high
-\textit{term frequency} in any
-document, but at the same time it will have a lower \textit{inverse document frequency} (almost close to $0$), which will nullify its effect on the quality of search results.
+\textit{term frequency} in almost all the
+documents, but at the same time it will have its \textit{inverse document frequency} almost close to $0$, which will nullify its effect on the quality of search results. \\
 
@@
 The implementation of the above scheme proved to be \emph{very} slow. It required
-too many computations and all of these were required to be done for each
-search result separately to compute its relevance weight. In an state of the
+too many computations and these were required to be done for each
+search result separately to compute its relevance weight. In a state of the
 art search application, the index would usually store precomputed \textit{tf-idf}
@@
 representing some of the most common sections found in man pages
-(see {\bf Listing 5}).
+(see {\bf Listing 5}) and a fast yet sophisticated ranking algorithm was adopted,
+to exploit this structured nature of the data. \\
 
-At this point a fast yet sophisticated ranking algorithm was adopted.
 \emph{Okapi BM25F} [15] is considered one of the most successful probabilistic
-models for information retrieval. \emph{Okapi BM25F} is based on \emph{tf-idf}
+models for information retrieval. It is based on \emph{tf-idf}
 scheme but it takes into account for the structure of the data. It allows for
 separate weights to be assigned for different parts of a structured document to
-come up with better relevance rankings. This scheme works very well for man pages
-because of their highly structured content. The algorithm is described in pseudo-code below. \textit{apropos} calls this function for each of the document
-obtained as part of the result set for the query and computes its relevancy
-weight. The documents are ranked in decreasing order of the weights returned
-from this function. \\
+come up with better relevance rankings. The exact implementation of this
+algorithm did not really provide any great results and therefore it had to be
+adapted and modified to suit the needs of \textit{apropos}, considering the
+structure of the database schema. The actual algorithm implemented is
+described in pseudo-code below. \textit{apropos} executes this function for each
+of the document obtained as part of the result set for the query and computes
+their relevancy weight. The documents are ranked in decreasing order of their
+weights. \\
 
 {\tt
-\lstset{language = sh, caption={Definition of important entities used in
+\lstset{language = XML, caption={Definition of important entities used in
 algorithm \ref{alg1}},}
@@
 \Require{Document {\tt d} whose weight needs to be computed}
+\Require {An array {\tt weights} consisting of preassigned weights for different
+columns of the FTS table}
 \State ${\tt tf} \gets 0.0$
@@
 \For {each column {\tt c} in the FTS table}
-\State $w \gets $ weight for column {\tt c}
+\State $w \gets weights[c] $
+\Comment {weight for column {\tt c}}
 \State $idf \gets idf + $ $log(\frac{ndoc}{ndocshitcount})\times w $
@@
 \section{Related Work}
-There are at least two projects which are related to this in some way.
 \begin{description}
@@
 \item[mandocdb] \hfill \\
-\textit{mandocdb} [12] is more in line with the goals of this project but it
+\textit{mandocdb} [12] is part of the \textit{mdocml} project and it is more in
+line with the goals of this project but it
 takes a novel approach. It indexes the keywords extracted from the man pages in a
@@
 of \textit{apropos} which performs search using this key-value store. The
-main key point of this implementation is that it exploits the semantic structure
+key point of this implementation is that it exploits the semantic structure
 but rather than indexing the complete content, it plucks out specific pieces of
 information from the man pages, for example author names, function names,
-header file names, etc.
-from the man pages. It is more sophisticated and much more useful than classic
+header file names, etc. It is more sophisticated and much more useful than
+classic
 \textit{apropos}, but it is still essentially a keyword lookup based
@@
 This project has been developed as part of \emph{Google Summer of Code 2011}
-[17], so thanks to \textbf{Google} for sponsoring it. Special thanks to
+[17], thanks to \textbf{Google} for sponsoring it. Special thanks to
 \textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
 project, he also helped by pointing out several issues in the parsing related
-code. We would like to thank \textbf{David Young} who was involved with
-this project closely and offered useful help and guidance throughout. A special
-thanks goes to \textbf{Thomas Klausner} who helped in writing and reviewing
-man pages for this project. Thanks to \textbf{Petra Zeidler} for administering
-the GSoC program for \textit{The NetBSD Foundation}. \\
+code. Thanks to \textbf{David Young} who was involved with
+this project closely and offered useful guidance and encouragement throughout. A
+special thanks goes to \textbf{Thomas Klausner} who helped in writing and
+reviewing the man pages for this project. Thanks to \textbf{Petra Zeidler} for
+administering the GSoC program for \textit{The NetBSD Foundation}. \\
 
@@
 
+\bibitem{21}
+\emph{Online manual page for mdoc(7)}
+\newline
+{\tt
+http://mdocml.bsd.lv/mdoc.7.html
+}
+
 \end{thebibliography}

### 2012-02-29 apropos_replacement.tex
Remove endnote
More fixes

@@
 \usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
+\usepackage{textcomp}
 %\usepackage[pdftex]{graphicx}
@@
 language=sh,
-basicstyle=\footnotesize,
+basicstyle=\footnotesize\ttfamily,
 numbers=none,
@@
 breakatwhitespace=false,
+upquote=true,
+escapechar=\%,
 title=\lstname
@@
 \and
-{\rm Joerg Sonnenberger}\\
+{\rm J\"org Sonnenberger}\\
 $<$joerg@NetBSD.org$>$
@@
 This paper discusses a new implementation of \textit{apropos} done by
-Abhinav Upadhyay and mentored by Joerg Sonnenberger as part of
+Abhinav Upadhyay and mentored by J\"org Sonnenberger as part of
 Google Summer of Code 2011, for The NetBSD Foundation. The goal of this project
@@
 
-{\tt \small
+{\small
 \lstset{language = XML, caption={No results for free form queries}}
 \begin{lstlisting}
-$ apropos ``add new user''
+$ apropos %\normalfont\upshape``%add new user%\normalfont\upshape''%
 add new user: nothing appropriate
 
-$ apropos ``get process status''
+$ apropos %\normalfont\upshape``%get process status%\normalfont\upshape''%
 get process status: nothing appropriate
 
-$ apropos ``termcap database''
+$ apropos %\normalfont\upshape``%termcap database%\normalfont\upshape''%
 termcap database: nothing appropriate
@@
 
-{\tt \small
+{\small
 \lstset{language = XML, caption={No support for stems or words with same root},}
 \begin{lstlisting}
-$ apropos ``make directories''
+$ apropos %\normalfont\upshape``%make directories%\normalfont\upshape"%
 mkdir (1) - make directories
 
-$ apropos ``make directory''
+$ apropos %\normalfont\upshape"%make directory%\normalfont\upshape"%
 make directory: nothing appropriate
 
-$ apropos ``upgrading package''
+$ apropos %\normalfont\upshape``%upgrading package%\normalfont\upshape''%
 pkg_add (1) - a utility for installing and
@@
 
-$ apropos ``upgrading packages''
+$ apropos %\normalfont\upshape``%upgrading packages%\normalfont\upshape''%
 upgrading packages: nothing appropriate
@@
 \begin{lstlisting}
-$ apropos ``copy strings''
+$ apropos %\normalfont\upshape``%copy strings%\normalfont\upshape''%
 stpcpy, stpncpy, strcpy, strncpy (3) - copy
@@
 
-$ apropos ``coppy strings''
+$ apropos %\normalfont\upshape``%coppy strings%\normalfont\upshape''%
 coppy strings: nothing appropriate
@@
 are stored on the file system in the from of hard (or symbolic) links and these
-have to be specified in the makefiles explicitly using the MLINKS mechanism. This
+have to be specified in the makefiles explicitly using the {\tt MLINKS}
+mechanism. This
 approach works fine but it is a mess from maintenance point of view.
@@
 }
-section holds more significance than if used inside of any other section. Similarly the description of various \textit{errno} values in the
+section holds more significance than if it is used elsewhere. Similarly the description of various \textit{errno} values in the
 \textit{intro(2)} man page has more important information than the mention of
@@
 out of man pages and index them in the form of an inverted index [4]. The index
-combined with a ranking algorithm which exploits the structured nature of the
-data to give back more relevant results to the user, can be used to build a
+can be combined with a ranking algorithm which exploits the structured nature of
+the
+data to give more relevant results to the user, and to build a
 high quality search interface for manual pages.
@@
 \item[Basic Natural Language Processing Support] \hfill \\
-When parsing the man pages and building the index, it is also possible to
-pre-process the tokens extracted from the man pages to support some of the very
+When parsing the man pages and building the index, tokens are preprocessed after
+extraction from the man pages to support some of the very
 basic natural language processing functionalities. In this implementation, the
@@
 In this implementation, additional metadata related to the man pages, for example
-an md5 hash, the device id, inode number and modification time
-of the man page files are indexed and stored.
-This allows for very fast and hassle free update of the index as new man pages are installed or the old ones are updated. \\
+an MD5 hash, the device id, inode number and modification time
+of the man page files are kept.
+This allows fast incremental update of the index as new man pages are installed or the old ones are updated. \\
 
@@
 This provides an option to get rid of all the hard or symbolic links of the man
-pages scattered throughout the filesystem, and also for clean up of the MLINKS
-mess in the makefiles.
+pages scattered throughout the filesystem, and also for clean up of the
+{\tt MLINKS} mess in the makefiles.
 \end{description}
@@
 tools and libraries which are battle tested and very successful.
-\textit{libmandoc} [6] from \textit{mdocml} [18] project has been used for
+\textit{libmandoc} [6] from the \textit{mdocml} [18] project has been used for
 parsing the man pages and \textit{sqlite} [7] for indexing and storing the parsed
@@
 
-In the second pass \textit{makemandb} generates md5 checksum of the files obtained from the previous stage and for each of these checksums, it checks in
-the db, whether this md5 checksum already exists in the db or not.
-If the md5 checksum is already present in the database, then this was just a false alarm and \textit{makemandb} does not need to parse the file, it simply updates the metadata of that file in the database.
-In case the md5 checksum of a file does not already exist in the database, then that means the file is either a newly installed man page or an older copy of a man page was updated,
+In the second pass \textit{makemandb} generates MD5 checksum of the files obtained from the previous stage and for each of these checksums, it checks in
+the db, whether this MD5 checksum already exists in the db or not.
+If the MD5 checksum is already present in the database, then this was just a false alarm and \textit{makemandb} does not need to parse the file, it simply updates the metadata of that file in the database.
+In case the MD5 checksum of a file does not already exist in the database, then that means the file is either a newly installed man page or an older copy of a man page was updated,
 \textit{makemandb} feeds such man pages to the parser and extracts interesting
@@
 simple. The FTS table consisted of 3 columns:
-{\tt
-name, name\_desc, desc
-}
+{\tt name}, {\tt name\_desc}, and {\tt desc}.
 The
@@
 more columns was done to represent the most commonly occurring sections in usual Unix man pages, for example
-{\tt NAME, DESCRIPTION, LIBRARY, RETURN VALUES, EXIT STATUS, ERRORS}
+{\tt NAME}, {\tt DESCRIPTION}, {\tt LIBRARY}, {\tt RETURN VALUES},
+{\tt EXIT STATUS}, {\tt ERRORS}
 etc. Such a decomposition allowed for an elaborate ranking scheme, which could
@@
 Another key aspect of any search application is to filter out or avoid stop-words
-. Words like \textit{``the'', ``a'', ``an'', ``'this''} etc. come under the
+. Words like \textit{``the'', ``a'', ``an'', ``this''} etc. come under the
 category of stop-words, these are the words which are \emph{very} commonly used
@@
   11. errors        ERRORS section
-  12. md5_hash      An md5 hash of the
+  12. md5_hash      An MD5 hash of the
                     contents of the man
@@
 requirements of the database index. As a concrete example, it took close
-to $90 MB$ to index about $8000$ documents. Without the precomputed weights, 
-the database size requirement was close to $45 MB$ for the same number of pages.
+to $90$ MB to index about $8000$ documents. Without the precomputed weights, 
+the database size requirement was close to $45$ MB for the same number of pages.
 \end{description}
@@
 This section shows results of some of the sample queries on new \textit{apropos}
-to demonstrate how it performs as compared to the traditional version.
-\endnote{Although the new \textit{apropos} by default returns 10
-results for a query but in the listings the output has been
-snipped to save space
-} \\
+to demonstrate how it performs as compared to the traditional version. \\
+%\footnote{Although the new \textit{apropos} by default returns 10
+%results for a query but in the listings the output has been
+%snipped to save space
+%} \\
 
-{\tt \small
+{ \small
 \lstset{language = XML, caption={Add new user},}
 \begin{lstlisting}
-$ apropos ``add new user''
+$ apropos %\normalfont\upshape``%add new user%\normalfont\upshape''%
 ssh-add(1)      adds private key identities to
@@
 \begin{lstlisting}
-$ apropos ``make directory''
+$ apropos %\normalfont\upshape``%make directory%\normalfont\upshape''%
 make(1) maintain program dependencies
@@
 \begin{lstlisting}
-$ apropos ``signal number to string''
+$ apropos %\normalfont\upshape``%signal number to string%\normalfont\upshape''%
 psignal(3)      system signal messages
@@
 
-\theendnotes
-
 \end{document}

### 2012-02-29 apropos_replacement.tex
Put the listings together on a separate page using single column layout.

@@
 they cannot search for keywords which are not usually specified in the title of
-a man page, for example a query like {\tt EINVAL} would return no results. \\
+a man page, for example a query like {\tt EINVAL} would return no results.
+See {\bf listing \ref{lst:noFreeFormQuery}} for concrete examples.  \\
+
+\subsection{Lack of basic language support}
+Another major limitation of the classical version of \textit{apropos} is that
+it is not smart enough to provide support for basic natural language processing
+constructs,
+like stemming or spelling corrections.
+As it can be seen in {\bf listing \ref{noStemming}},
+while \textit{apropos} returns the correct result for the query
+\textit{``make directories''}, it fails when the keyword \textit{``directory''}
+is used in place of \textit{``directories''}, even though the two words are based
+on same root word. \\
+
+Similarly, it is very common for users to misspell keywords in a query and \textit{apropos} has no support for detecting it and offering any useful behavior either (see {\bf listing \ref{noSpell}}).
+
+\subsection{Unintelligible Output}
+Because of the way \textit{apropos} works, sometimes its output can be
+unintelligible and it can be very hard for the user to identify relevant results, see {\bf listing \ref{unintelligibleOutput}} for an example. \\
 
 {\small
-\lstset{language = XML, caption={No results for free form queries}}
-\begin{lstlisting}
+\lstset{language = XML, caption={No results for free form queries},
+label={lst:noFreeFormQuery}}
+\begin{lstlisting}[float=*]
 $ apropos %\normalfont\upshape``%add new user%\normalfont\upshape''%
@@
 
-\subsection{Lack of basic language support}
-Another major limitation of the classical version of \textit{apropos} is that
-it is not smart enough to provide support for basic natural language processing
-constructs,
-like stemming or spelling corrections.
-For example in the following listing it can be seen
-that while \textit{apropos} returns the correct result for the query
-\textit{``make directories''}, it fails when the keyword \textit{``directory''}
-is used in place of \textit{``directories''}, even though the two words are based
-on same root word. \\
-
 {\small
-\lstset{language = XML, caption={No support for stems or words with same root},}
-\begin{lstlisting}
+\lstset{language = XML, caption={No support for stems or words with same root},
+label=noStemming}
+\begin{lstlisting}[float=*]
 $ apropos %\normalfont\upshape``%make directories%\normalfont\upshape"%
@@
 $ apropos %\normalfont\upshape``%upgrading package%\normalfont\upshape''%
-pkg_add (1) - a utility for installing and
-upgrading software package distributions
+pkg_add (1) - a utility for installing and upgrading software package distributions
 
@@
 
-Similarly, it is very common for users to misspell keywords in a query and \textit{apropos} has no support for it either.
-
 {\tt \small
-\lstset{language = sh, caption={No spelling correction},}
-\begin{lstlisting}
+\lstset{language = sh, caption={No spelling correction}, label=noSpell}
+\begin{lstlisting}[float=*]
 $ apropos %\normalfont\upshape``%copy strings%\normalfont\upshape''%
-stpcpy, stpncpy, strcpy, strncpy (3) - copy
-strings
+stpcpy, stpncpy, strcpy, strncpy (3) - copy strings
 
@@
 
-\subsection{Unintelligible Output}
-Because of the way \textit{apropos} works, sometimes its output can be
-unintelligible and it can be very hard for the user to identify relevant results. \\
-
 {\tt \small
-\lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},}
-\begin{lstlisting}
+\lstset{language = sh, caption={Unintelligible output of \textit{apropos(1)}},
+label=unintelligibleOutput}
+\begin{lstlisting}[float=*]
 $ apropos power
@@
 simple. The FTS table consisted of 3 columns:
-{\tt name}, {\tt name\_desc}, and {\tt desc}.
-The
+{\tt name}, {\tt name\_desc}, and {\tt desc}. The
 {\tt
 name
-}
-and
+}and
 {\tt
 name\_desc
-}
-columns stored the name of the man page and the one line description from the
+}columns stored the name of the man page and the one line description from the
 {\tt
 NAME
-}
-section respectively, while the
+}section respectively, while the
 {\tt
 desc
-}
-column stored the content from the rest of the sections. This approach worked
+}column stored the content from the rest of the sections. This approach worked
 quite well for a small set of man pages (for example the 4000 or so man pages in
@@
 assign different weights to each of these columns, based on their relevancy. The
-final schema of the database is shown in {\bf Listing 5}
+final schema of the database is shown in {\bf listing \ref{schema}}
+{\tt \small
+\lstset{language = XML, caption={Database Schema}, label={schema}}
+\begin{lstlisting}[float=*]
+The Database has three tables:
+1. mandb
+2. mandb_meta
+3. mandb_links
+
+(1) mandb:
+    The main FTS table which contains all the content parsed from man pages
+
+  COLUMN NAME       DESCRIPTION
+  1. section        Section number
+  2. name           The name of the man page  
+  3. name_desc      Short description from NAME section  
+  4. desc           Contains the content from DESCRIPTION section and any other
+                    section which is not stored in a separate column.
+  5. lib            The LIBRARY section
+  6. return_vals    RETURN VALUES section
+  7. env            ENVIRONMENT section
+  8. files          FILES section
+  9. exit_status    EXIT STATUS section
+  10. diagnostics   DIAGNOSTICS section
+  11. errors        ERRORS section
+  12. md5_hash      An MD5 hash of the contents of the man page (UNIQUE).
+
+(2) mandb_meta:
+    This table maintains essential metadata of all the indexed man page files.
+
+  COLUMN NAME       DESCRIPTION
+  1. device         (dev_t)Logical device number from stat(2)
+  2. inode          (ino_t)Inode number from stat(2)
+  3. mtime          Last modification time from stat(2)
+  4. file           Absolute path name (UNIQUE constraint)
+  5. md5_hash       MD5 Hash of the man page file (UNIQUE)
+  6. id             A unique integer ID referring to a page in mandb (PRIMARY KEY)
+
+(3) mandb_links:
+    This is an index of all the hard/soft links of the man pages. The list of
+    the aliases is usually obtained from the multiple .Nm entries in the NAME
+    section of a man page.
+
+  COLUMN NAME       DESCRIPTION
+  1. link           The name of the hard/soft link (UNIQUE index) 
+  2. target         Name of the target page to which the link points  
+  3. section        The section number
+  4. machine        The machine architecture (if any) for which the page is
+                    relevant.
+\end{lstlisting}
+}
+
 \end{description}
@@
 not come under the category of stop-words. \\
-
-{\tt \small
-\lstset{language = XML, caption={Database Schema},}
-\begin{lstlisting}
-The Database has three tables at present:
-1. mandb
-2. mandb_meta
-3. mandb_links
-
-(1) mandb:
-    The main FTS table which contains all
-    the content parsed from man pages
-
-  COLUMN NAME       DESCRIPTION
-  1. section        Section number
-  2. name           The name of the page  
-  3. name_desc      Short description from
-                    NAME section  
-  4. desc           Contains the content
-                    from DESCRIPTION
-                    section and any other
-                    section which is not
-                    stored in a separate
-                    column.
-  5. lib            The LIBRARY section
-  6. return_vals    RETURN VALUES section
-  7. env            ENVIRONMENT section
-  8. files          FILES section
-  9. exit_status    EXIT STATUS section
-  10. diagnostics   DIAGNOSTICS section
-  11. errors        ERRORS section
-  12. md5_hash      An MD5 hash of the
-                    contents of the man
-                    page (UNIQUE).
-(2) mandb_meta:
-    This table maintains essential
-    metadata of all the indexed
-    man page files.
-
-  COLUMN NAME       DESCRIPTION
-  1. device         (dev_t)Logical device
-                    number from stat(2)
-  2. inode          (ino_t)Inode number
-                    from stat(2)
-  3. mtime          Last modification time
-                    from stat(2)
-  4. file           Absolute path name
-                    (UNIQUE constraint)
-  5. md5_hash       MD5 Hash of the man
-                    page
-  6. id             A unique integer ID
-                    referring to a page
-                    in mandb (PRIMARY KEY)
-
-(3) mandb_links:
-    This is an index of all the hard/soft
-    links of the man pages. The list of
-    the linked pages is usually obtained 
-    from the multiple .Nm entries in the
-    page.
-
-  COLUMN NAME       DESCRIPTION
-  1. link           The name of the hard/
-                    soft link (UNIQUE index) 
-  2. target         Name of the target
-                    page to which it
-                    points  
-  3. section        The section number  
-  4. machine        The machine
-                    architecture (if any)
-                    for which the page is
-                    relevant.
-\end{lstlisting}
-}
 
@@
 
+\pagebreak
 \section{Results}
-This section shows results of some of the sample queries on new \textit{apropos}
-to demonstrate how it performs as compared to the traditional version. \\
-%\footnote{Although the new \textit{apropos} by default returns 10
-%results for a query but in the listings the output has been
-%snipped to save space
-%} \\
-
-{ \small
-\lstset{language = XML, caption={Add new user},}
-\begin{lstlisting}
-$ apropos %\normalfont\upshape``%add new user%\normalfont\upshape''%
-ssh-add(1)      adds private key identities to
-the authentication agent...on the command line.
-If any file requires a passphrase, ssh-add asks
-for the passphrase from the user. The
-passphrase is read from the user's tty. ssh-add
-retries the last passphrase if multiple
-identity files are given...
-
-chpass(1)       add or change user database
-information
-add or change user database information
-
-useradd(8)      add a user to the system
-The useradd utility adds a user to the system,
-creating and populating a home directory if
-necessary. Any skeleton files will be provided
-for the new user if they exist in the skel-dir
-directory (see the k option). Default...
-.
-.
-.
-\end{lstlisting}
-}
-
-{\tt \small
-\lstset{language = XML, caption={make directory},}
-\begin{lstlisting}
-$ apropos %\normalfont\upshape``%make directory%\normalfont\upshape''%
-make(1) maintain program dependencies
-...CURDIR A path to the directory where make
-was executed. Refer to the description of PWD
-for more details. MAKE The name that make was
-executed with argv[0].
-For compatibility make also sets .MAKE with the
-same value. The...
-
-mkdir(1)        make directories
-make directories
-
-ln(1)   make links
-...a directory in which to place the link;
-otherwise it is placed in the current directory
-If only the directory is specified, the link
-will be made to the last component of
-source_file . Given more than two arguments,
-ln makes...
-
-mkfifo(1)       make fifos
-make fifos...of a=rw mkfifo requires write
-permission in the parent directory. mkfifo
-exits 0 if successful, and >0 if an...
-
-mkdir(2)        make a directory file
-...will contain the directory has been
-exhausted. EDQUOT The user's quota of
-inodes on the file system on which the
-directory is being created has been
-exhausted. EIO An I/O error occurred
-while making the directory entry or...
-\end{lstlisting}
-}
-
-{\tt \small
-\lstset{language = XML, caption={signal number to string},}
-\begin{lstlisting}
-$ apropos %\normalfont\upshape``%signal number to string%\normalfont\upshape''%
-psignal(3)      system signal messages
-...the signal number is not recognized
-sigaction(2) , the string Unknown signal
-is produced. The psiginfo function produces
-the same output as the psignal function,
-only it uses the signal number information
-from the si argument. The message strings can...
-
-intro(2)        introduction to system calls
-and error numbers
-...undefined signal to a signal(3) or kill(2)
-function). 23 ENFILE Too many open files in
-system . Maximum number...shell. Pathname A
-path name is a NUL -terminated character
-string starting with an optional slash,
-followed by zero or...
-
-dump_lfs(8)     filesystem backup
-...low estimates of the number of blocks to
-write, the number of tapes it...a string
-containing embedded formatting commands for
-strftime(3). The total formatted string
-is...in. If dump_lfs rdump_lfs receives a
-SIGINFO signal (see the status argument of
-stty...
-\end{lstlisting}
-}
-
-\begin{figure*}[htp]
-\begin{center}
-\includegraphics [scale=0.36]{/home/abhinav/development/AsiaBSDCon/spell.png}
-\caption{The spell corrector and the CGI frontend in action}
-\label{}
-\end{center}
-\end{figure*}
+{\bf Listing \ref{newUser}}, {\bf \ref{makeDirectory}}, and {\bf \ref{signal} } show results of some of the sample queries on new \textit{apropos}
+to demonstrate how it performs as compared to the traditional version.
+\endnote{Although the new \textit{apropos} by default returns 10
+results for a query but in the listings the output has been
+snipped to save space
+} \\
 
@@
 \end{description}
+
+{ \small
+\lstset{language = XML, caption={Add new user}, label={newUser}}
+\begin{lstlisting}[float=*]
+$ apropos %\normalfont\upshape``%add new user%\normalfont\upshape''%
+ssh-add(1)      adds private key identities to the authentication agent...on the command line.
+If any file requires a passphrase, ssh-add asks for the passphrase from the user. The passphrase
+is read from the user's tty. ssh-add retries the last passphrase if multiple identity files are
+given...
+
+chpass(1)       add or change user database information
+add or change user database information
+
+useradd(8)      add a user to the system
+The useradd utility adds a user to the system, creating and populating a home directory if
+necessary. Any skeleton files will be provided for the new user if they exist in the skel-dir
+directory (see the k option). Default...
+.
+.
+.
+\end{lstlisting}
+}
+
+{\tt \small
+\lstset{language = XML, caption={make directory}, label={makeDirectory}}
+\begin{lstlisting}[float=*]
+$ apropos %\normalfont\upshape``%make directory%\normalfont\upshape''%
+make(1) maintain program dependencies
+...CURDIR A path to the directory where make was executed. Refer to the description of PWD for
+more details. MAKE The name that make was executed with argv[0]. For compatibility make also sets
+.MAKE with the same value. The...
+
+mkdir(1)        make directories
+make directories
+
+ln(1)   make links
+...a directory in which to place the link; otherwise it is placed in the current directory If
+only the directory is specified, the link will be made to the last component of source_file
+. Given more than two arguments, ln makes...
+
+mkfifo(1)       make fifos
+make fifos...of a=rw mkfifo requires write permission in the parent directory. mkfifo exits 0 if
+successful, and >0 if an...
+
+mkdir(2)        make a directory file
+...will contain the directory has been exhausted. EDQUOT The user's quota of inodes on the file
+system on which the directory is being created has been exhausted. EIO An I/O error occurred
+while making the directory entry or...
+\end{lstlisting}
+}
+
+{\tt \small
+\lstset{language = XML, caption={signal number to string}, label={signal}}
+\begin{lstlisting}[float=*]
+$ apropos %\normalfont\upshape``%signal number to string%\normalfont\upshape''%
+psignal(3)      system signal messages
+...the signal number is not recognized sigaction(2) , the string Unknown signal is produced. The
+psiginfo function produces the same output as the psignal function, only it uses the signal
+number information from the si argument. The message strings can...
+
+intro(2)        introduction to system calls and error numbers
+...undefined signal to a signal(3) or kill(2) function). 23 ENFILE Too many open files in system.
+Maximum number...shell. Pathname A path name is a NUL -terminated character string starting with
+an optional slash, followed by zero or...
+
+dump_lfs(8)     filesystem backup
+...low estimates of the number of blocks to write, the number of tapes it...a string containing
+embedded formatting commands for strftime(3). The total formatted string is...in. If dump_lfs
+rdump_lfs receives a SIGINFO signal (see the status argument of stty...
+\end{lstlisting}
+}
+
+\begin{figure*}[htp]
+\begin{center}
+\includegraphics [scale=0.36]{/home/abhinav/development/AsiaBSDCon/spell.png}
+\caption{The spell corrector and the CGI frontend in action}
+\label{}
+\end{center}
+\end{figure*}
 
@@
 
+\pagebreak
 \section{Acknowledgement}
@@
 \end{thebibliography}
+\theendnotes
 

### 2012-02-29 apropos_replacement.tex
Remove unnecessary text
Some preformance stats

@@
 \section{Limitations of Conventional \textit{apropos}}
-In this section results of some sample query searches from
-the classical version of \textit{apropos} are shown and their shortcomings are
-analyzed. \\
 
@@
 an MD5 hash, the device id, inode number and modification time
-of the man page files are kept.
+of the man page files are kept in the database.
 This allows fast incremental update of the index as new man pages are installed or the old ones are updated. \\
@@
 \section{Results}
+\subsection{Performance of apropos}
 {\bf Listing \ref{newUser}}, {\bf \ref{makeDirectory}}, and {\bf \ref{signal} } show results of some of the sample queries on new \textit{apropos}
@@
 snipped to save space
-} \\
+}
+In \textbf{Figure 1}, the spell corrector can be seen in action along with the web
+interface that was developed using \textit{apropos-utils}. \\
 
-In \textbf{Figure 1} the spell corrector can be seen in action along with the web
-interface that was developed using \textit{apropos-utils}. \\
+\subsection{Performance of makemandb} 
+On a modern desktop hardware, \textit{makemandb} takes about 25 seconds
+to index 4000 man pages, and the size of this index is $15$ MB. When 
+the number of man pages is increased to 6100 by including some packages from
+\textit{pkgsrc}, the time taken by \textit{makemandb} grows to about 50 seconds
+and the size of the database index grows to $27$ MB. \\
 
@@
 \end{description}
-
+\pagebreak
 \section{Availability}
@@
 
-\pagebreak
 \section{Acknowledgement}
